---
title: "Hausaufgaben"
description: |
  Kontraste zwischen Grundschule und Gymnasium
author:
  - name: Jürgen Schneider 
    url: https://uni-tuebingen.de/de/28915
    affiliation: Universität Tübingen
  - name: Britta Kohler
date: "`r Sys.Date()`"
output: 
  radix::radix_article:
    toc: yes
    toc_depth: 2
---

```{r setup, echo=T}
knitr::opts_chunk$set(echo = T, message = F, warning = F)
library(rio)
library(tidyverse)
library(lubridate)
library(ggstance)
library(mice)
library(miceadds)
library(naniar)
library(psych)
library(ggrepel)
library(BayesFactor)
library(bindata)
library(pander)
library(corrgram)
library(hrbrthemes)
library(MASS)
library(bain)

R.Version()
```

# Datenvorbereitung

```{r import, include=T}
# import
gym <- rio::import("data/gym.xls")
gs <- rio::import("data/gs.xls")
```

## Grundschule

```{r wrangling gs}

gs <- gs %>%
  dplyr::filter(`Laufende\nNummer` != "Beispiel") %>%
  mutate(id = as.numeric(`Laufende\nNummer`))

## Korrektur von Daten auf Basis der Abweichungen
 # Falschberechnungen der `Min Beginn seit Std-Anfang` (id == 189, 248, 329) werden übersprungen
 # da die selbst berechnete variable `beg_hw_min` verwendet wird
 # aufgrund der unterschiedlichen Zeitzone muss zusätzlich noch eine h drauf gerechnet werden
gs[which(gs$id == 105), "Uhrzeit Beginn HA Vergabe"] <- "1899-12-31 11:48:00"    # Tippfehler, nochmals in FB nachgeschaut
gs[which(gs$id == 105), "Uhrzeit Ende Vergabe"] <- "1899-12-31 11:51:00"         # Tippfehler, nochmals in FB nachgeschaut
gs[which(gs$id == 120), "Uhrzeit Beginn HA Vergabe"] <- "1899-12-31 11:58:00"    # Tippfehler, nochmals in FB nachgeschaut
gs[which(gs$id == 168), "Uhrzeit Beginn HA Vergabe"] <- "1899-12-31 11:43:00"    # Tippfehler, nochmals in FB nachgeschaut
gs[which(gs$id == 250), "Uhrzeit Ende Vergabe"] <- "1899-12-31 12:33:00"         # Tippfehler, nochmals in FB nachgeschaut
gs[which(gs$id == 187), "Uhrzeit Beginn der Std laut Plan"] <- "1899-12-31 09:20:00" # Tippfehler, nochmals in FB nachgeschaut
gs[which(gs$id == 187), "Uhrzeit Ende der Std laut Plan"] <- "1899-12-31 10:50:00" # Tippfehler, nochmals in FB nachgeschaut
gs[which(gs$id == 187), "Uhrzeit Beginn HA Vergabe"] <- "1899-12-31 10:24:00"    # Tippfehler, nochmals in FB nachgeschaut
gs[which(gs$id == 187), "Uhrzeit Ende Vergabe"] <- "1899-12-31 10:40:00"         # Tippfehler, nochmals in FB nachgeschaut
gs[which(gs$id == 307), "Uhrzeit Ende Vergabe"] <- "1899-12-31 10:16:00"         # Tippfehler, nochmals in FB nachgeschaut
gs[which(gs$id == 315), "Uhrzeit Ende Vergabe"] <- "1899-12-31 11:55:00"         # Tippfehler, nochmals in FB nachgeschaut
gs[which(gs$id == 220), "Ankündigung"] <- 1 # Tippfehler
gs[which(gs$id == 198), "L schreibt"] <- 1 # Tippfehler 
gs[which(gs$id == 330), "L will Notation"] <- NA # Wert "9" gibt es nicht, nicht nachvollziehbar, welcher Wert plausibel ist


# new var
gs <- gs %>%
  mutate(beg_plan = hm(format(strptime(`Uhrzeit Beginn der Std laut Plan`,"%Y-%m-%d %H:%M:%S"),'%H:%M')),
         end_plan = hm(format(strptime(`Uhrzeit Ende der Std laut Plan`,"%Y-%m-%d %H:%M:%S"),'%H:%M')),
         beg_act  = hm(format(strptime(`Uhrzeit Realer Beginn der Std`,"%Y-%m-%d %H:%M:%S"),'%H:%M')),
         beg_hw   = hm(format(strptime(`Uhrzeit Beginn HA Vergabe`,"%Y-%m-%d %H:%M:%S"),'%H:%M')),
         end_hw   = hm(format(strptime(`Uhrzeit Ende Vergabe`,"%Y-%m-%d %H:%M:%S"),'%H:%M')),
         stunde   = lubridate::hour(end_plan - beg_plan)*60 + lubridate::minute(end_plan - beg_plan),     # geplante Länge der Unterrichtsstunde
         beg_hw_min = lubridate::hour(beg_hw - beg_plan)*60 + lubridate::minute(beg_hw - beg_plan),       # Beginn der HA relativ zu GEPLANTEM h-Anfang
         dau_hw_min = lubridate::hour(end_hw - beg_hw)*60 + lubridate::minute(end_hw - beg_hw),
         lh_ank   = `Ankündigung`,
         lh_auf   = `L verlangt Aufmerk`,
         lh_nen   = `L nennt`,
         lh_sch   = `L schreibt`,
         lh_erl   = `L erläutert`,
         lh_wfr   = `L will Fragen`,
         lh_bfr   = `L beantwortet`,
         lh_wno   = `L will Notation`,
         lh_ano   = `L achtet Notat`,
         sh_auf = `S aufmerksam`,
         sh_mel = `S melden`,
         sh_fra = `S fragen`,
         sh_not = `S notieren`)
```


## Gymnasium

```{r wrangling gym}
gym <- gym %>%
  mutate(id = as.numeric(`Laufende\nNummer`))

gym[which(gym$id == 141 |
          gym$id == 148 |
          gym$id == 149 |
          gym$id == 150 |
          gym$id == 164 |
          gym$id == 175 |
          gym$id == 180 |
          gym$id == 181 |
          gym$id == 182 |
          gym$id == 188 |
          gym$id == 189), "L schreibt"] <- 1 # Tippfehler, in FB nachgeschaut


# new var
gym <- gym %>%
  mutate(beg_hw_min = `Min Beginn`,
         dau_hw_min = `HA stellen Dauer`,
         stunde     = case_when(Doppelstundenmodell == 0 ~ 45,
                                Doppelstundenmodell == 1 ~ 90),
         Schulart = "Gymnasium",
         lh_ank   = `Ankündigung`,
         lh_auf   = `L sorg Aufmerk`,
         lh_nen   = `L nennt`,
         lh_sch   = `L schreibt`,
         lh_erl   = `Erläuterung gesamt`,
         lh_wfr   = `L will Fragen`,
         lh_bfr   = `L beantwortet`,
         lh_wno   = `L will Notation`,
         lh_ano   = `L achtet Notat`,
         sh_auf = `S aufmerksam`,    
         sh_mel = `S melden`,
         sh_fra = `Fragen gesamt`,
         sh_not = `S notieren`)
```

## Erstellung gemeinsamer Datensatz

```{r gemeins}
gs_p <- gs %>%
  dplyr::select(beg_hw_min, dau_hw_min, stunde, Schulart, Klassenstufe, lh_ank, lh_auf, lh_nen,
         lh_sch, lh_erl, lh_wfr, lh_bfr, lh_wno, lh_ano, sh_auf, sh_mel, sh_fra, sh_not)

gym_p <- gym %>%
  dplyr::select(beg_hw_min, dau_hw_min, stunde, Schulart, Klassenstufe, lh_ank, lh_auf, lh_nen,
         lh_sch, lh_erl, lh_wfr, lh_bfr, lh_wno, lh_ano, sh_auf, sh_mel, sh_fra, sh_not)

p_data <- rbind(gs_p, gym_p)

# filter away the 10 cross grade classes as they are difficult to analyze 
# (combine characteristics of two grades in one)
p_data <- p_data %>%
  dplyr::filter(Klassenstufe != "1_2" | is.na(Klassenstufe)) %>%
  mutate(Klassenstufe = as.numeric(Klassenstufe))
```


# Imputation der fehlenden Daten
```{r prozentuale haeufigkeiten}
### SKALENNIVEAUS ###
  # lh_ank: dichotom [0,1]
  # lh_auf: dichotom [0,1]
  # lh_nen: dichotom [0,1]
  # lh_sch: dichotom [0,1]
  # lh_erl: dichotom [0,1]
  # lh_wfr: dichotom [0,1]
  # lh_bfr: metrisch, absolutskaliert, schief
  # lh_wno: dichotom [0,1]
  # lh_ano: dichotom [0,1]
  # sh_auf: ordinalskaliert [1:5]
  # sh_mel: metrisch, absolutskaliert, schief
  # sh_fra: metrisch, absolutskaliert, schief
  # sh_not: metrisch, intervllskaliert, bimodal
```

```{r imput}
vis_miss(p_data)
gg_miss_upset(p_data)
```

## Choices

__imputation model__
```{r model}
p_data$Schulart <- as.factor(p_data$Schulart)
p_data$Klassenstufe <- as.numeric(p_data$Klassenstufe)

model_tab <- data.frame(variable = c("beg_hw_min", "dau_hw_min", "stunde", "Schulart", "Klassenstufe", "lh_ank", "lh_auf", "lh_nen", "lh_sch", 
                                     "lh_erl", "lh_wfr", "lh_bfr", "lh_wno", "lh_ano", "sh_auf", "sh_mel", "sh_fra", "sh_not"),
                        'scale type' = c("metric", "metric", "metric", "nominal", "metric", "binary", "binary", "binary", "binary", 
                                         "binary", "binary", "metric", "binary", "binary", "metric", "metric", "metric", "metric"),
                        method = c("pmm", "pmm", "pmm", "polyreg", "pmm", "logreg", "logreg", "logreg", "logreg", 
                                   "logreg", "logreg", "pmm", "logreg", "logreg", "pmm", "pmm", "pmm", "pmm"))

pander(model_tab)

```


```{r def model}
# Defining methods
meth <- c("pmm", "pmm", "pmm", "polyreg", "pmm", "logreg", "logreg", "logreg", "logreg", 
          "logreg", "logreg", "pmm", "logreg", "logreg", "pmm", "pmm", "pmm", "pmm")
```

__number of imputations__  
1000  

```{r n imput}
m <- 1000
```

__selection of predictors__
```{r pred}
# cor(y = p_data[,-4], x = !is.na(p_data[,-4]), use = "pair")
corrgram(p_data, lower.panel = "panel.pie", upper.panel = "panel.cor")
```

```{r pred spec}
# set predictor specifications
ini <- mice(p_data, 
            maxit = 0, 
            m = m,
            meth = meth,
            seed = 666
            )

pred <- ini$predictorMatrix
pred[,"stunde"] <- 0 # stunde highly correlated with beg_hw_min
pred[,"lh_bfr"] <- 0 # lh_bfr highly correlated with sh_fra
```


__variables that are function of other variables__  
None.  

__which variables to impute__  
All.  

__number of iterations__  

20  

```{r maxit}
maxit <- 20
```


## imputation

```{r imp, message=F, comment=F, warning=F, cache=F}
imp <- mice(p_data, 
            maxit = maxit, 
            m = m,
            meth = meth,
            pred = pred,
            seed = 666,
            printFlag = F
            )
```

## check imputation

__plausible values__
```{r plaus}
## will produce one plot for each imputation (200) on each variable
## uncomment if interested, otherwise I spare the space
# lattice::stripplot(imp, pch = 20, cex = 1.2)
```
All values seem plausible.

__check convergence__
```{r conv}
plot(imp)
```

# Bayes Factor Design Analysis für Kreuztabellen

Bayes Factor Design Analysis zur Bestimmung des BF Thresholds.  

## Effektstärke
  
Aufgrund fehlender Referenzwerte nehmen wir eine Effektstärke von $\varphi=.2$ an. Dieser liegt zwischen einem kleinen ($\varphi=.1$) und mittleren ($\varphi=.3$) Effekt nach Cohen (1988).

```{r bfda crosstab hyp}
true_hyp <- c("H0 is true", "H1 is true") # two possibilities
phi <- c(0, .2)    # determine effect sizes for hypotheses
```

## Anzahl Simulationen

Es werden 1000 Simulationen durchgeführt. Aufgrund der Robustheit der Ergebnisse in diesem Bereich, verzichteten wir auf eine größere Anzahl an Simulationen.

```{r bfda crosstab nsim}
n_sim <- 1000 # number of simulations
```

## Ergebnisse Simulation

```{r bfda crosstab, fig.height=12, fig.width=12}
sim_cor_results <- data.frame()   # set up data frame for results

for(j in true_hyp) {                               # loop over both hypotheses
  if (j == "H0 is true")
  bincorr <- matrix(c(1,phi[1],phi[1],1), ncol=2)  # create correlation matrix for H0
  if (j == "H1 is true")
  bincorr <- matrix(c(1,phi[2],phi[2],1), ncol=2)  # create correlation matrix for H1
  
  for (n in 1:n_sim) {
    sim_df <- rmvbin(n = 510,
                     margprob = c(0.5, 0.5),
                     bincorr = bincorr)
    
    sim_imp_m <- matrix(table(sim_df[,1], sim_df[,2]), 2, 2)
    sim_fit <- contingencyTableBF(sim_imp_m, sampleType="indepMulti",fixedMargin = "cols")
    sim_cor_results[n+ifelse(j == "H0 is true", 0, n_sim), "BayesFactor"] <- extractBF(sim_fit)$bf
    sim_cor_results[n+ifelse(j == "H0 is true", 0, n_sim), "trueH"] <- j
    rm(sim_imp_m, sim_fit)
  }
}

# categorize if result is correct, incorrect or inconclusive
sim_cor_results <- sim_cor_results %>%
  mutate(BF3 = case_when(
                    BayesFactor >= 3 & trueH == "H0 is true" ~ "incorrect",
                    BayesFactor < 3 & BayesFactor > (1/3) & trueH == "H0 is true" ~ "inconclusive",
                    BayesFactor <= (1/3) & trueH == "H0 is true" ~ "correct",
                    BayesFactor >= 3 & trueH == "H1 is true" ~ "correct",
                    BayesFactor < 3 & BayesFactor > (1/3) & trueH == "H1 is true" ~ "inconclusive",
                    BayesFactor <= (1/3) & trueH == "H1 is true" ~ "incorrect"),
         BF5 = case_when(
                    BayesFactor >= 5 & trueH == "H0 is true" ~ "incorrect",
                    BayesFactor < 5 & BayesFactor > (1/5) & trueH == "H0 is true" ~ "inconclusive",
                    BayesFactor <= (1/5) & trueH == "H0 is true" ~ "correct",
                    BayesFactor >= 5 & trueH == "H1 is true" ~ "correct",
                    BayesFactor < 5 & BayesFactor > (1/5) & trueH == "H1 is true" ~ "inconclusive",
                    BayesFactor <= (1/5) & trueH == "H1 is true" ~ "incorrect"),
         BF10 = case_when(
                    BayesFactor >= 10 & trueH == "H0 is true" ~ "incorrect",
                    BayesFactor < 10 & BayesFactor > (1/10) & trueH == "H0 is true" ~ "inconclusive",
                    BayesFactor <= (1/10) & trueH == "H0 is true" ~ "correct",
                    BayesFactor >= 10 & trueH == "H1 is true" ~ "correct",
                    BayesFactor < 10 & BayesFactor > (1/10) & trueH == "H1 is true" ~ "inconclusive",
                    BayesFactor <= (1/10) & trueH == "H1 is true" ~ "incorrect"),
         )

# pivot into long data frame for plot
sim_cor_results_l <- pivot_longer(sim_cor_results, 
                                  cols = 3:5, 
                                  names_to = "BF Threshold",
                                  values_to = "decision") 
# order factor for plot
sim_cor_results_l$`BF Threshold` <- factor(sim_cor_results_l$`BF Threshold`, levels = c("BF3", "BF5", "BF10"))


# hrbrthemes::import_roboto_condensed()

ggplot(sim_cor_results_l, aes(trueH, fill = decision)) +
    geom_bar(position = "fill") +
    geom_text(aes(label=round(..count../n_sim*100), y= ..count../n_sim),
    position =position_stack(vjust = 0.5), stat= "count",
    color = "white", size = 5) +
    coord_flip() +
    facet_wrap(~`BF Threshold`, ncol = 1) +
    labs(title = "Results of the Bayes Factor Design Analysis",
         subtitle = "For three different Bayes Factors",
         caption = paste("In % (rounded), based on", n_sim, "simulations")) +
    xlab("True Hypothesis") +
    scale_fill_viridis_d() +
    theme_ipsum_rc()
```

Die Ergebnisse zeigen, dass bei einem BF von 3 kaum falsch-positive Ergebnisse zustande kommen (~1%) und die Power jeweils zufriedenstellend bzw. sehr hoch ist. Es ist somit nicht nötig einen höheren BF zu verweneden, um falsch-positive Ergebnisse zu vermeiden. Höhere BFs hätten zudem den Nachteil, dass vermehrt inkonklusive Ergebnisse auftreten. Wir verwenden bei der Auswertung der binären Zusammenhänge (Kreuztabellen) somit einen Threshold von $BF=3$ bzw. $BF=\frac{1}{3}$.


# Bayes Factor Design Analysis für t-Tests

Bayes Factor Design Analysis zur Bestimmung des BF Thresholds.  

## Effektstärke
  
Aufgrund fehlender Referenzwerte nehmen wir eine Effektstärke von $d=.35$ an. Dieser liegt zwischen einem kleinen ($d=.2$) und mittleren ($d=.5$) Effekt nach Cohen (1988).

```{r bfda ttest hyp}
true_hyp <- c("H0 is true", "H1 is true") # two possibilities
true_d <- c(0, .35)    # determine effect sizes for hypotheses
```

## Anzahl Simulationen

Es werden 1000 Simulationen durchgeführt. Aufgrund der Robustheit der Ergebnisse in diesem Bereich, verzichteten wir auf eine größere Anzahl an Simulationen.

```{r bfda ttest nsim}
n_sim <- 1000 # number of simulations
```

## Ergebnisse Simulation

```{r bfda ttest, fig.height=12, fig.width=12}
sim_ttest_results <- data.frame()   # set up data frame for results

for(j in true_hyp) {                            # loop over both hypotheses

  for (n in 1:n_sim) {                             # loop over all simulations
      sim_ttest_df <- data.frame(mvrnorm(n = 510,                         # fixed n of 510
                                     mu = if(j == "H0 is true")
                                          c(0,true_d[1]) else              # create data set for H0
                                          if(j == "H1 is true")
                                          c(0,true_d[2]),             # create data set for H1
                                     Sigma = matrix(c( 1, .5,         # vcov matrix
                                                      .5,  1),
                                                      2, 2)))
      
    # pivot longer to insert it into a lm
    sim_ttest_df_l <- pivot_longer(sim_ttest_df, 1:2, names_to = "group", values_to = "dependentVar")
    
    ### LINEAR MODEL ############################################ #
    # compute the means of each group
    sim_fit_ttest <- lm(dependentVar ~ group-1, 
                        data = sim_ttest_df_l)
    ### BAIN #################################################### #    
    # generating hypotheses
    hypotheses <- "groupX1 = groupX2; groupX1 < groupX2"   #H1 and H2 respectively
    
    bf_ttest <- bain(sim_fit_ttest, 
                     hypothesis = hypotheses
                     )
    
    sim_ttest_results[n+ifelse(j == "H0 is true", 0, n_sim),"BayesFactor"] <- bf_ttest$BFmatrix[2,1]  # BF(H2,H1)
    sim_ttest_results[n+ifelse(j == "H0 is true", 0, n_sim), "trueH"] <- j
    rm(bf_ttest, sim_fit_ttest, sim_ttest_df, sim_ttest_df_l)
  }
}


# categorize if result is correct, incorrect or inconclusive
sim_ttest_results <- sim_ttest_results %>%
  mutate(BF3 = case_when(
                    BayesFactor >= 3 & trueH == "H0 is true" ~ "incorrect",
                    BayesFactor < 3 & BayesFactor > (1/3) & trueH == "H0 is true" ~ "inconclusive",
                    BayesFactor <= (1/3) & trueH == "H0 is true" ~ "correct",
                    BayesFactor >= 3 & trueH == "H1 is true" ~ "correct",
                    BayesFactor < 3 & BayesFactor > (1/3) & trueH == "H1 is true" ~ "inconclusive",
                    BayesFactor <= (1/3) & trueH == "H1 is true" ~ "incorrect"),
         BF5 = case_when(
                    BayesFactor >= 5 & trueH == "H0 is true" ~ "incorrect",
                    BayesFactor < 5 & BayesFactor > (1/5) & trueH == "H0 is true" ~ "inconclusive",
                    BayesFactor <= (1/5) & trueH == "H0 is true" ~ "correct",
                    BayesFactor >= 5 & trueH == "H1 is true" ~ "correct",
                    BayesFactor < 5 & BayesFactor > (1/5) & trueH == "H1 is true" ~ "inconclusive",
                    BayesFactor <= (1/5) & trueH == "H1 is true" ~ "incorrect"),
         BF10 = case_when(
                    BayesFactor >= 10 & trueH == "H0 is true" ~ "incorrect",
                    BayesFactor < 10 & BayesFactor > (1/10) & trueH == "H0 is true" ~ "inconclusive",
                    BayesFactor <= (1/10) & trueH == "H0 is true" ~ "correct",
                    BayesFactor >= 10 & trueH == "H1 is true" ~ "correct",
                    BayesFactor < 10 & BayesFactor > (1/10) & trueH == "H1 is true" ~ "inconclusive",
                    BayesFactor <= (1/10) & trueH == "H1 is true" ~ "incorrect"),
         )

# pivot into long data frame for plot
sim_ttest_results_l <- pivot_longer(sim_ttest_results, 
                                    cols = 3:5, 
                                    names_to = "BF Threshold",
                                    values_to = "decision") 
# order factor for plot
sim_ttest_results_l$`BF Threshold` <- factor(sim_ttest_results_l$`BF Threshold`, levels = c("BF3", "BF5", "BF10"))


# hrbrthemes::import_roboto_condensed()

ggplot(sim_ttest_results_l, aes(trueH, fill = decision)) +
    geom_bar(position = "fill") +
    geom_text(aes(label=round(..count../n_sim*100), y= ..count../n_sim),
    position =position_stack(vjust = 0.5), stat= "count",
    color = "white", size = 5) +
    coord_flip() +
    facet_wrap(~`BF Threshold`, ncol = 1) +
    labs(title = "Results of the Bayes Factor Design Analysis",
         subtitle = "For three different Bayes Factors",
         caption = paste("In % (rounded), based on", n_sim, "simulations")) +
    xlab("True Hypothesis") +
    scale_fill_viridis_d() +
    theme_ipsum_rc()
```

Hier zeigen sich bei einem $N=510$ und einem angenommenen Cohen's $d=.35$ ebenfalls (nahezu) keine falsch-positiven Ergebnisse. Somit wird auch hier auf ein Threshold von $BF=3$ bzw. $BF=\frac{1}{3}$ verwendet.


# Zeitpunkt der HA-Vergabe

__Deskriptive Daten__

```{r deskriptiv zeit}
pander::panderOptions('digits', 3)
## 45 Minuten Stunden ################ #
# alle Schulstunden mit Länge 45min herausfiltern
schulart45 <- p_data %>% 
  dplyr::filter(stunde == 45)

# Deskriptiven Werte für diese Stunden
descriptives45 <-  p_data %>%
    dplyr::filter(stunde == 45) %>%
    dplyr::select(beg_hw_min, dau_hw_min) %>%
    psych::describeBy(group = schulart45$Schulart)

pander::pander(descriptives45)

# Modus
dens_45gs <- schulart45 %>%      # filter only measured cases
  dplyr::filter(!is.na(beg_hw_min) & Schulart == "Grundschule") #filter for Grundschule
dens_45gs <- density(dens_45gs$beg_hw_min)   # get density curve

dens_45gy <- schulart45 %>%      # filter only measured cases
  dplyr::filter(!is.na(beg_hw_min) & Schulart == "Gymnasium") #filter for Gymnasium 
dens_45gy <- density(dens_45gy$beg_hw_min)   # get density curve
paste("Modus der Hausaufgabenvergabe in 45min Stunden Grundschule =", round(dens_45gs$x[which.max(dens_45gs$y)], 1))
paste("Modus der Hausaufgabenvergabe in 45min Stunden Gymnasium =", round(dens_45gy$x[which.max(dens_45gy$y)], 1))



## 90 Minuten Stunden ################ #
# alle Schulstunden mit Länge 45min herausfiltern
schulart90 <- p_data %>% 
  dplyr::filter(stunde == 90)

# Deskriptiven Werte für diese Stunden
descriptives90 <-  p_data %>%
    dplyr::filter(stunde == 90) %>%
    dplyr::select(beg_hw_min, dau_hw_min) %>%
    psych::describeBy(group = schulart90$Schulart)

pander::pander(descriptives90)

# Modus
dens_90gs <- schulart90 %>%      # filter only measured cases
  dplyr::filter(!is.na(beg_hw_min) & Schulart == "Grundschule") #filter for Grundschule
dens_90gs <- density(dens_90gs$beg_hw_min)   # get density curve

dens_90gy <- schulart90 %>%      # filter only measured cases
  dplyr::filter(!is.na(beg_hw_min) & Schulart == "Gymnasium") #filter for Gymnasium 
dens_90gy <- density(dens_90gy$beg_hw_min)   # get density curve
paste("Modus der Hausaufgabenvergabe in 90min Stunden Grundschule =", round(dens_90gs$x[which.max(dens_90gs$y)], 1))
paste("Modus der Hausaufgabenvergabe in 90min Stunden Gymnasium =", round(dens_90gy$x[which.max(dens_90gy$y)], 1))

```

## 45min Stunden  


```{r plots zeitpunkt 45, cache=F}
#### IMPUTATION #### #
# separate Imputation für 45min
p_data_45 <- p_data %>%
    dplyr::filter(stunde==45)

imp45 <- mice(p_data_45, 
              maxit = maxit, 
              m = m,
              meth = meth,
              pred = pred,
              seed = 666,
              printFlag = F
              )

#### Compute BFs within informed hypotheses framework (bain) ##################################### #

### for bain: compute vcov by hand ###
# create data frame to collect var and cov for each imputation
vcov_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

mean_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

# sample size per group
samp_gr <- table(mice::complete(imp45)$Schulart)

## loop over all m imputations
for(i in 1:m) {
  # fit model
  fit_lm <- lm(beg_hw_min ~ Schulart-1, data = mice::complete(imp45, i))
  
  var_lm <- summary(fit_lm)$sigma**2 # get variance of the means (VOM)
  vcov_df[i, "Grundschule"] <- var_lm/samp_gr["Grundschule"] # compute VOM per group
  vcov_df[i, "Gymnasium"] <- var_lm/samp_gr["Gymnasium"] # compute VOM per group
  
  # collect estimates of the means
  mean_df[i, "Grundschule"] <- coef(fit_lm)["SchulartGrundschule"]
  mean_df[i, "Gymnasium"] <- coef(fit_lm)["SchulartGymnasium"]
  
  rm(fit_lm, var_lm) # clean up, because we like it tidy in here
}


## make var matrices 
# compute the mean over var
vcov_df <- vcov_df %>%
        summarize_all(mean)

# create matrices
mat1 <- matrix(vcov_df$Grundschule, 1, 1)
mat2 <- matrix(vcov_df$Gymnasium, 1, 1)

variances <- list(mat1, mat2)

## compute mean of estimates
bf_data <- mean_df %>%
        summarize_all(mean)
bf_data <- as.numeric(bf_data)
names(bf_data) <- c("Grund", "Gym")

## BAIN ##### #
# generating hypotheses
hypotheses <- "Gym = Grund; Gym < Grund; Gym > Grund"

bf_45 <- bain(bf_data, 
              hypothesis = hypotheses,
              n = samp_gr,           # size of the groups
              Sigma = variances,     # matrices of residual variances of groups
              group_parameters = 1,  # there is 1 group specific parameter (the mean in each group)
              joint_parameters = 0   # there are no parameters that apply to each of the groups (e.g. the regression coefficient of a covariate)
              )

print(bf_45)
print(bf_45$BFmatrix)



###### DESCRIPTIVE PLOT ############################################### #

## Awesome Rainvloud plots, check out source:
# Allen M, Poggiali D, Whitaker K et al. Raincloud plots: a multi-platform tool for 
#           robust data visualization [version 1; peer review: 2 approved]. 
#           Wellcome Open Res 2019, 4:63. DOI: 10.12688/wellcomeopenres.15191.1
source("R_rainclouds.R")

ggplot(p_data%>%dplyr::filter(stunde == 45), aes(x="", y = beg_hw_min, fill = Schulart, colour = Schulart)) +
                geom_flat_violin(position = position_nudge(x = 0, y = 0), adjust = 1.6, trim = FALSE, alpha = .3) +
                geom_boxplot(aes(x=""), position = position_nudge(x = c(.49, .54), y = 0), 
                             outlier.shape = NA, alpha = .5, width = .04, colour = "black") +
                geom_hline(yintercept = 45, linetype = "dashed", colour = "#696f71", size = 1) +
                scale_colour_brewer(palette = "Set1")+
                scale_fill_brewer(palette = "Set1") +
                scale_y_continuous(expand = c(0, 0), breaks = c(0, 10,20,30,40,45,50,60), limits = c(0, 65)) +
                scale_x_discrete(expand = c(0, 0)) +
                ylab("Minuten seit geplantem Stundenbeginn") +
                xlab("% Häufigkeit") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7")) +
                coord_flip()
      

```

## 90min Stunden  

Basierend auf untersuchten (nicht-fehlenden) Daten.  

```{r plots zeitpunkt 90, cache=F}
#### IMPUTATION #### #
# separate Imputation für 90min
p_data_90 <- p_data %>%
    dplyr::filter(stunde==90)

imp90 <- mice(p_data_90, 
              maxit = maxit, 
              m = m,
              meth = meth,
              pred = pred,
              seed = 666,
              printFlag = F
              )

#### Compute BFs within informed hypotheses framework (bain) ##################################### #

### for bain: compute vcov by hand ###
# create data frame to collect var and cov for each imputation
vcov_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

mean_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

# sample size per group
samp_gr <- table(mice::complete(imp90)$Schulart)


## loop over all m imputations
for(i in 1:m) {
  fit_lm <- lm(beg_hw_min ~ Schulart-1, data = mice::complete(imp90, i))
  
  var_lm <- summary(fit_lm)$sigma**2 # get variance of the means (VOM)
  vcov_df[i, "Grundschule"] <- var_lm/samp_gr["Grundschule"] # compute VOM per group
  vcov_df[i, "Gymnasium"] <- var_lm/samp_gr["Gymnasium"] # compute VOM per group
  
  # collect estimates of the means
  mean_df[i, "Grundschule"] <- coef(fit_lm)["SchulartGrundschule"]
  mean_df[i, "Gymnasium"] <- coef(fit_lm)["SchulartGymnasium"]
  
  rm(fit_lm, var_lm) # clean up, because we like it tidy in here
}

## make var matrices 
# compute the mean over var
vcov_df <- vcov_df %>%
        summarize_all(mean)

# create matrices
mat1 <- matrix(vcov_df$Grundschule, 1, 1)
mat2 <- matrix(vcov_df$Gymnasium, 1, 1)

variances <- list(mat1, mat2)

## compute mean of estimates
bf_data <- mean_df %>%
        summarize_all(mean)
bf_data <- as.numeric(bf_data)
names(bf_data) <- c("Grund", "Gym")


## BAIN ##### #
# generating hypotheses
hypotheses <- "Gym = Grund; Gym < Grund; Gym > Grund"

bf_90 <- bain(bf_data, 
              hypothesis = hypotheses,
              n = samp_gr,           # size of the groups
              Sigma = variances,     # matrices of residual variances of groups
              group_parameters = 1,  # there is 1 group specific parameter (the mean in each group)
              joint_parameters = 0   # there are no parameters that apply to each of the groups (e.g. the regression coefficient of a covariate)
              )

print(bf_90)
print(bf_90$BFmatrix)


###### DESCRIPTIVE PLOT ############################################### #

ggplot(p_data%>%dplyr::filter(stunde == 90), 
       aes(x="", y = beg_hw_min, fill = Schulart, colour = Schulart)) +
                geom_flat_violin(position = position_nudge(x = 0, y = 0), 
                                 adjust = 1.6, trim = FALSE, alpha = .3) +
                geom_boxplot(aes(x=""), position = position_nudge(x = c(.50, .56), y = 0), 
                             outlier.shape = NA, alpha = .5, width = .05, colour = "black") +
                geom_hline(yintercept = 90, linetype = "dashed", colour = "#696f71", size = 1) +
                scale_colour_brewer(palette = "Set1")+
                scale_fill_brewer(palette = "Set1") +
                scale_y_continuous(expand = c(0, 0), 
                                   breaks = c(0, 10,20,30,40,50,60,70,80,90), 
                                   limits = c(0,95)) +
                scale_x_discrete(expand = c(0, 0)) +
                ylab("Minuten seit geplantem Stundenbeginn") +
                xlab("% Häufigkeit") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7")) +
                coord_flip()
```


# Zeitbedarf HA  

## 45min Stunden

```{r plots zeitbedarf 45}

#### Compute BFs within informed hypotheses framework (bain) ##################################### #

### for bain: compute vcov by hand ###
# create data frame to collect var and cov for each imputation
vcov_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

mean_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

# sample size per group
samp_gr <- table(mice::complete(imp45)$Schulart)


## loop over all m imputations
for(i in 1:m) {
  fit_lm <- lm(dau_hw_min ~ Schulart-1, data = mice::complete(imp45, i))
  
  var_lm <- summary(fit_lm)$sigma**2 # get variance of the means (VOM)
  vcov_df[i, "Grundschule"] <- var_lm/samp_gr["Grundschule"] # compute VOM per group
  vcov_df[i, "Gymnasium"] <- var_lm/samp_gr["Gymnasium"] # compute VOM per group
  
  # collect estimates of the means
  mean_df[i, "Grundschule"] <- coef(fit_lm)["SchulartGrundschule"]
  mean_df[i, "Gymnasium"] <- coef(fit_lm)["SchulartGymnasium"]
  
  rm(fit_lm, var_lm) # clean up, because we like it tidy in here
}

## make var matrices 
# compute the mean over var
vcov_df <- vcov_df %>%
        summarize_all(mean)

# create matrices
mat1 <- matrix(vcov_df$Grundschule, 1, 1)
mat2 <- matrix(vcov_df$Gymnasium, 1, 1)

variances <- list(mat1, mat2)

## compute mean of estimates
bf_data <- mean_df %>%
        summarize_all(mean)
bf_data <- as.numeric(bf_data)
names(bf_data) <- c("Grund", "Gym")


## BAIN ##### #
# generating hypotheses
hypotheses <- "Gym = Grund; Gym < Grund; Gym > Grund"


bf_45 <- bain(bf_data, 
              hypothesis = hypotheses,
              n = samp_gr,           # size of the groups
              Sigma = variances,     # matrices of residual variances of groups
              group_parameters = 1,  # there is 1 group specific parameter (the mean in each group)
              joint_parameters = 0   # there are no parameters that apply to each of the groups (e.g. the regression coefficient of a covariate)
              )

print(bf_45)
print(bf_45$BFmatrix)



###### DESCRIPTIVE PLOT ############################################### #

ggplot(p_data%>%dplyr::filter(stunde == 45), aes(x=Schulart, y = dau_hw_min, fill = Schulart)) +
                geom_flat_violin(position = position_nudge(x = .1, y = 0), 
                                 adjust = 1.6, trim = FALSE, alpha = .3, colour = NA) +
                geom_point(position = position_jitter(width = .05), size = 1, alpha = 0.5, aes(color=Schulart)) +
                geom_boxplot(position = position_nudge(x = -.15, y = 0), 
                             outlier.shape = NA, alpha = .5, width = .1, colour = "black") +
                scale_colour_brewer(palette = "Set1")+
                scale_y_continuous(expand = c(0, 0)) +
                scale_fill_brewer(palette = "Set1") +
                ylab("Minuten") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))

```

## 90min Stunden

```{r plots zeitbedarf 90}

#### Compute BFs within informed hypotheses framework (bain) ##################################### #

### for bain: compute vcov by hand ###
# create data frame to collect var and cov for each imputation
vcov_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

mean_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

# sample size per group
samp_gr <- table(mice::complete(imp90)$Schulart)


## loop over all m imputations
for(i in 1:m) {
  fit_lm <- lm(dau_hw_min ~ Schulart-1, data = mice::complete(imp90, i))
  
  var_lm <- summary(fit_lm)$sigma**2 # get variance of the means (VOM)
  vcov_df[i, "Grundschule"] <- var_lm/samp_gr["Grundschule"] # compute VOM per group
  vcov_df[i, "Gymnasium"] <- var_lm/samp_gr["Gymnasium"] # compute VOM per group
  
  # collect estimates of the means
  mean_df[i, "Grundschule"] <- coef(fit_lm)["SchulartGrundschule"]
  mean_df[i, "Gymnasium"] <- coef(fit_lm)["SchulartGymnasium"]
  
  rm(fit_lm, var_lm) # clean up, because we like it tidy in here
}

## make var matrices 
# compute the mean over var
vcov_df <- vcov_df %>%
        summarize_all(mean)

# create matrices
mat1 <- matrix(vcov_df$Grundschule, 1, 1)
mat2 <- matrix(vcov_df$Gymnasium, 1, 1)

variances <- list(mat1, mat2)

## compute mean of estimates
bf_data <- mean_df %>%
        summarize_all(mean)
bf_data <- as.numeric(bf_data)
names(bf_data) <- c("Grund", "Gym")

## BAIN ##### #
# generating hypotheses
hypotheses <- "Gym = Grund; Gym < Grund; Gym > Grund"

bf_90 <- bain(bf_data, 
              hypothesis = hypotheses,
              n = samp_gr,           # size of the groups
              Sigma = variances,     # matrices of residual variances of groups
              group_parameters = 1,  # there is 1 group specific parameter (the mean in each group)
              joint_parameters = 0   # there are no parameters that apply to each of the groups (e.g. the regression coefficient of a covariate)
              )

print(bf_90)
print(bf_90$BFmatrix)


###### DESCRIPTIVE PLOT ############################################### #

ggplot(p_data%>%dplyr::filter(stunde == 90), aes(x=Schulart, y = dau_hw_min, fill = Schulart)) +
                geom_flat_violin(position = position_nudge(x = .1, y = 0), 
                                 adjust = 1.6, trim = FALSE, alpha = .3, colour = NA) +
                geom_point(position = position_jitter(width = .05), size = 1, alpha = 0.5, aes(color=Schulart)) +
                geom_boxplot(position = position_nudge(x = -.15, y = 0), 
                             outlier.shape = NA, alpha = .5, width = .1, colour = "black") +
                scale_colour_brewer(palette = "Set1")+
                scale_y_continuous(expand = c(0, 0)) +
                scale_fill_brewer(palette = "Set1") +
                ylab("Minuten") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))

```


# Häufigkeiten der Lehrpersonen-/SuS-Handlungen

__Deskriptive Daten__

```{r deskriptiv Angebot}
descriptives <-  p_data %>%
    dplyr::select(lh_ank, lh_auf, lh_nen, lh_sch,
                  lh_erl, lh_wfr, lh_wno, lh_ano,
                  lh_bfr, sh_auf, sh_mel, sh_fra, sh_not) %>%
    psych::describeBy(group = p_data$Schulart)

panderOptions('digits', 3)
pander::pander(descriptives)

```


## L kündigt HA an

### Prädiktor Schulart

```{r ank BF}
# Compute density of BFs
cor_results <- data.frame()

for (i in 1:m) {
  imp_m <- matrix(table(mice::complete(imp, i)$lh_ank,     # create contingency table
                        mice::complete(imp, i)$Schulart), 2, 2)
  fit <- contingencyTableBF(imp_m, sampleType="indepMulti",
                            fixedMargin = "cols")          # GS and GY as fixed
  cor_results[i,"lh_ank-Schulart"] <- extractBF(fit)$bf    # save BF in data frame
  
  chains <- posterior(fit, iterations = 1000)  # get posterior probabilities
  showMerkm_givenGS <- chains[,"pi[2,1]"] / chains[,"pi[*,1]"]  # compute ratio for GS
  showMerkm_givenGY <- chains[,"pi[2,2]"] / chains[,"pi[*,2]"]  # compute ratio for GY
  cor_results[i,"prob_GSminusGY"] <- mean(mcmc(showMerkm_givenGS - showMerkm_givenGY)) # Markov Chain
                                                                         # Monte Carlo of differences
  
  rm(imp_m, fit, chains)
}

# show summary of BFs
summary(cor_results[,"lh_ank-Schulart"])  

# plot BFs distribution
ggplot(cor_results, aes(x = `lh_ank-Schulart`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_ank-Schulart`, y=""), 
                            height = 1, width = 0, alpha = .3, 
                            size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))

# plot difference of 
summary(cor_results[,"prob_GSminusGY"])
```

### Prädiktor Klassenstufe

```{r ank Klassenstufe}
# Compute density of BFs
kl_results <- data.frame()

for (i in 1:m) {
  fit <- correlationBF(y = mice::complete(imp, i)$lh_ank,    # correlation
                       x = mice::complete(imp, i)$Klassenstufe)
  kl_results[i,"lh_ank-Klassenstufe"] <- extractBF(fit)$bf    # save BF in data frame
  
  rm(fit)
}

# show summary of BFs
summary(kl_results[,"lh_ank-Klassenstufe"])  


# plot BFs distribution
ggplot(kl_results, aes(x = `lh_ank-Klassenstufe`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_ank-Klassenstufe`, y=""), 
                            height = 1, width = 0, alpha = .3, 
                            size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))
```

### Plot der deskriptiven Daten

```{r ank plot}
###### DESCRIPTIVE PLOT ############################################### #
# plot (non-missing) values as descriptive
lh_ank_p <- p_data %>%
  dplyr::filter(!is.na(lh_ank) & !is.na(Klassenstufe)) %>%
  group_by(Klassenstufe) %>%
  mutate(length = length(lh_ank)) %>%
  summarize(lh_ank = mean(lh_ank, na.rm=T),
            length_n = mean(length)) %>%
  ungroup() %>%
  mutate(Klassenstufe = factor(Klassenstufe, levels = c("1", "1_2", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")),
         Schulart = as.factor(case_when(
                      Klassenstufe == "1" ~ "Grundschule",
                      Klassenstufe == "1_2" ~ "Grundschule",
                      Klassenstufe == "2" ~ "Grundschule",
                      Klassenstufe == "3" ~ "Grundschule",
                      Klassenstufe == "4" ~ "Grundschule",
                      TRUE ~ "Gymnasium"
         )))

ggplot(lh_ank_p, aes(x = Klassenstufe, y = lh_ank, color = Schulart)) + 
  geom_line(aes(group = NA), color = "grey", size = 1) +
  geom_point(aes(size = length_n)) +
  geom_text(aes(label = paste(round(lh_ank*100,0), "%"), vjust = 3)) +
  scale_y_continuous(limits = c(0,1), expand = c(0,0)) +
  geom_rect(aes(xmin = 0, xmax = 4.5, ymin = -Inf, ymax = Inf), fill = "pink", alpha = .01, color = NA) +
  geom_rect(aes(xmin = 4.5, xmax = 14, ymin = -Inf, ymax = Inf), fill = "#BFEFFF", alpha = .01, color = NA) +
  xlab("Klassenstufe") +
  ylab("% Häufigkeit") +
  labs(size = "Anzahl\neingegangener\nStunden") +
  theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7")) 
  
  
```


## L fordert Aufmerksamkeit

### Prädiktor Schulart

```{r haeufigkeiten auf}
# Compute density of BFs
for (i in 1:m) {
  imp_m <- matrix(table(mice::complete(imp, i)$lh_auf, mice::complete(imp, i)$Schulart), 2, 2)
  fit <- contingencyTableBF(imp_m, sampleType="indepMulti",fixedMargin = "cols")
  cor_results[i,"lh_auf-Schulart"] <- extractBF(fit)$bf
    
  chains <- posterior(fit, iterations = 1000)  # get posterior probabilities
  showMerkm_givenGS <- chains[,"pi[2,1]"] / chains[,"pi[*,1]"]  # compute ratio for GS
  showMerkm_givenGY <- chains[,"pi[2,2]"] / chains[,"pi[*,2]"]  # compute ratio for GY
  cor_results[i,"prob_GSminusGY"] <- mean(mcmc(showMerkm_givenGS - showMerkm_givenGY)) # Markov Chain Monte Carlo of differences
  
  rm(imp_m, fit, chains)
}

summary(cor_results[,"lh_auf-Schulart"])

ggplot(cor_results, aes(x = `lh_auf-Schulart`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_auf-Schulart`, y=""), height = 1, width = 0, alpha = .3, size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))

# plot difference of 
summary(cor_results[,"prob_GSminusGY"])
```

### Prädiktor Klassenstufe

```{r auf Klassenstufe}
# Compute density of BFs
kl_results <- data.frame()

for (i in 1:m) {
  fit <- correlationBF(y = mice::complete(imp, i)$lh_auf,    # correlation
                       x = mice::complete(imp, i)$Klassenstufe)
  kl_results[i,"lh_auf-Klassenstufe"] <- extractBF(fit)$bf    # save BF in data frame
  
  rm(fit)
}

# show summary of BFs
summary(kl_results[,"lh_auf-Klassenstufe"])  

# plot BFs distribution
ggplot(kl_results, aes(x = `lh_auf-Klassenstufe`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_auf-Klassenstufe`, y=""), 
                            height = 1, width = 0, alpha = .3, 
                            size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))
```

### Plot der deskriptiven Daten

```{r auf plot}


###### DESCRIPTIVE PLOT ############################################### #

lh_auf_p <- p_data %>%
  dplyr::filter(!is.na(lh_auf) & !is.na(Klassenstufe)) %>%
  group_by(Klassenstufe) %>%
  mutate(length = length(lh_auf)) %>%
  summarize(lh_auf = mean(lh_auf, na.rm=T),
            length_n = mean(length)) %>%
  ungroup() %>%
  mutate(Klassenstufe = factor(Klassenstufe, levels = c("1", "1_2", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")),
         Schulart = as.factor(case_when(
                      Klassenstufe == "1" ~ "Grundschule",
                      Klassenstufe == "1_2" ~ "Grundschule",
                      Klassenstufe == "2" ~ "Grundschule",
                      Klassenstufe == "3" ~ "Grundschule",
                      Klassenstufe == "4" ~ "Grundschule",
                      TRUE ~ "Gymnasium"
         )))

ggplot(lh_auf_p, aes(x = Klassenstufe, y = lh_auf, color = Schulart)) + 
  geom_line(aes(group = NA), color = "grey", size = 1) +
  geom_point(aes(size = length_n)) +
  geom_text(aes(label = paste(round(lh_auf*100,0), "%"), vjust = 3)) +
  scale_y_continuous(limits = c(0,1), expand = c(0,0)) +
  geom_rect(aes(xmin = 0, xmax = 4.5, ymin = -Inf, ymax = Inf), fill = "pink", alpha = .01, color = NA) +
  geom_rect(aes(xmin = 4.5, xmax = 14, ymin = -Inf, ymax = Inf), fill = "#BFEFFF", alpha = .01, color = NA) +
  xlab("Klassenstufe") +
  ylab("% Häufigkeit") +
  labs(size = "Anzahl\neingegangener\nStunden") +
  theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7")) 
```


## L nennt HA

### Prädiktor Schulart

```{r haeufigkeiten nen}
# Compute density of BFs
for (i in 1:m) {
  imp_m <- matrix(table(mice::complete(imp, i)$lh_nen, mice::complete(imp, i)$Schulart), 2, 2)
  fit <- contingencyTableBF(imp_m, sampleType="indepMulti",fixedMargin = "cols")
  cor_results[i,"lh_nen-Schulart"] <- extractBF(fit)$bf
    
  chains <- posterior(fit, iterations = 1000)  # get posterior probabilities
  showMerkm_givenGS <- chains[,"pi[2,1]"] / chains[,"pi[*,1]"]  # compute ratio for GS
  showMerkm_givenGY <- chains[,"pi[2,2]"] / chains[,"pi[*,2]"]  # compute ratio for GY
  cor_results[i,"prob_GSminusGY"] <- mean(mcmc(showMerkm_givenGS - showMerkm_givenGY)) # Markov Chain Monte Carlo of differences
  
  rm(imp_m, fit, chains)
}

summary(cor_results[,"lh_nen-Schulart"])

ggplot(cor_results, aes(x = `lh_nen-Schulart`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_nen-Schulart`, y=""), height = 1, width = 0, alpha = .3, size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))

# plot difference of 
summary(cor_results[,"prob_GSminusGY"])
```

### Prädiktor Klassenstufe

```{r nen Klassenstufe}
# Compute density of BFs
kl_results <- data.frame()

for (i in 1:m) {
  fit <- correlationBF(y = mice::complete(imp, i)$lh_nen,    # correlation
                       x = mice::complete(imp, i)$Klassenstufe)
  kl_results[i,"lh_nen-Klassenstufe"] <- extractBF(fit)$bf    # save BF in data frame
  
  rm(fit)
}

# show summary of BFs
summary(kl_results[,"lh_nen-Klassenstufe"])  

# plot BFs distribution
ggplot(kl_results, aes(x = `lh_nen-Klassenstufe`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_nen-Klassenstufe`, y=""), 
                            height = 1, width = 0, alpha = .3, 
                            size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))
```

### Plot der deskriptiven Daten

```{r nen plot}


###### DESCRIPTIVE PLOT ############################################### #

lh_nen_p <- p_data %>%
  dplyr::filter(!is.na(lh_nen) & !is.na(Klassenstufe)) %>%
  group_by(Klassenstufe) %>%
  mutate(length = length(lh_nen)) %>%
  summarize(lh_nen = mean(lh_nen, na.rm=T),
            length_n = mean(length)) %>%
  ungroup() %>%
  mutate(Klassenstufe = factor(Klassenstufe, levels = c("1", "1_2", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")),
         Schulart = as.factor(case_when(
                      Klassenstufe == "1" ~ "Grundschule",
                      Klassenstufe == "1_2" ~ "Grundschule",
                      Klassenstufe == "2" ~ "Grundschule",
                      Klassenstufe == "3" ~ "Grundschule",
                      Klassenstufe == "4" ~ "Grundschule",
                      TRUE ~ "Gymnasium"
         )))

ggplot(lh_nen_p, aes(x = Klassenstufe, y = lh_nen, color = Schulart)) + 
  geom_line(aes(group = NA), color = "grey", size = 1) +
  geom_point(aes(size = length_n)) +
  geom_text(aes(label = paste(round(lh_nen*100,0), "%"), vjust = 3)) +
  scale_y_continuous(limits = c(0,1), expand = c(0,0)) +
  geom_rect(aes(xmin = 0, xmax = 4.5, ymin = -Inf, ymax = Inf), fill = "pink", alpha = .01, color = NA) +
  geom_rect(aes(xmin = 4.5, xmax = 14, ymin = -Inf, ymax = Inf), fill = "#BFEFFF", alpha = .01, color = NA) +
  xlab("Klassenstufe") +
  ylab("% Häufigkeit") +
  labs(size = "Anzahl\neingegangener\nStunden") +
  theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7")) 
```


## L schreibt HA an

### Prädiktor Schulart

```{r haeufigkeiten sch}
# Compute density of BFs
for (i in 1:m) {
  imp_m <- matrix(table(mice::complete(imp, i)$lh_sch, mice::complete(imp, i)$Schulart), 2, 2)
  fit <- contingencyTableBF(imp_m, sampleType="indepMulti",fixedMargin = "cols")
  cor_results[i,"lh_sch-Schulart"] <- extractBF(fit)$bf
    
  chains <- posterior(fit, iterations = 1000)  # get posterior probabilities
  showMerkm_givenGS <- chains[,"pi[2,1]"] / chains[,"pi[*,1]"]  # compute ratio for GS
  showMerkm_givenGY <- chains[,"pi[2,2]"] / chains[,"pi[*,2]"]  # compute ratio for GY
  cor_results[i,"prob_GSminusGY"] <- mean(mcmc(showMerkm_givenGS - showMerkm_givenGY)) # Markov Chain Monte Carlo of differences
  
  rm(imp_m, fit, chains)
}

summary(cor_results[,"lh_sch-Schulart"])

ggplot(cor_results, aes(x = `lh_sch-Schulart`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_sch-Schulart`, y=""), height = 1, width = 0, alpha = .3, size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))


# plot difference of 
summary(cor_results[,"prob_GSminusGY"])
```

### Prädiktor Klassenstufe

```{r sch Klassenstufe}
# Compute density of BFs
kl_results <- data.frame()

for (i in 1:m) {
  fit <- correlationBF(y = mice::complete(imp, i)$lh_sch,    # correlation
                       x = mice::complete(imp, i)$Klassenstufe)
  kl_results[i,"lh_sch-Klassenstufe"] <- extractBF(fit)$bf    # save BF in data frame
  
  rm(fit)
}

# show summary of BFs
summary(kl_results[,"lh_sch-Klassenstufe"])  

# plot BFs distribution
ggplot(kl_results, aes(x = `lh_sch-Klassenstufe`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_sch-Klassenstufe`, y=""), 
                            height = 1, width = 0, alpha = .3, 
                            size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))
```

### Plot der deskriptiven Daten

```{r sch plot}

###### DESCRIPTIVE PLOT ############################################### #

lh_sch_p <- p_data %>%
  dplyr::filter(!is.na(lh_sch) & !is.na(Klassenstufe)) %>%
  group_by(Klassenstufe) %>%
  mutate(length = length(lh_sch)) %>%
  summarize(lh_sch = mean(lh_sch, na.rm=T),
            length_n = mean(length)) %>%
  ungroup() %>%
  mutate(Klassenstufe = factor(Klassenstufe, levels = c("1", "1_2", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")),
         Schulart = as.factor(case_when(
                      Klassenstufe == "1" ~ "Grundschule",
                      Klassenstufe == "1_2" ~ "Grundschule",
                      Klassenstufe == "2" ~ "Grundschule",
                      Klassenstufe == "3" ~ "Grundschule",
                      Klassenstufe == "4" ~ "Grundschule",
                      TRUE ~ "Gymnasium"
         )))

ggplot(lh_sch_p, aes(x = Klassenstufe, y = lh_sch, color = Schulart)) + 
  geom_line(aes(group = NA), color = "grey", size = 1) +
  geom_point(aes(size = length_n)) +
  geom_text(aes(label = paste(round(lh_sch*100,0), "%"), vjust = 3)) +
  scale_y_continuous(limits = c(0,1), expand = c(0,0)) +
  geom_rect(aes(xmin = 0, xmax = 4.5, ymin = -Inf, ymax = Inf), fill = "pink", alpha = .01, color = NA) +
  geom_rect(aes(xmin = 4.5, xmax = 14, ymin = -Inf, ymax = Inf), fill = "#BFEFFF", alpha = .01, color = NA) +
  xlab("Klassenstufe") +
  ylab("% Häufigkeit") +
  labs(size = "Anzahl\neingegangener\nStunden") +
  theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7")) 

```


## L erläutert HA  

### Prädiktor Schulart

```{r haeufigkeiten erl}
# Compute density of BFs
for (i in 1:m) {
  imp_m <- matrix(table(mice::complete(imp, i)$lh_erl, mice::complete(imp, i)$Schulart), 2, 2)
  fit <- contingencyTableBF(imp_m, sampleType="indepMulti",fixedMargin = "cols")
  cor_results[i,"lh_erl-Schulart"] <- extractBF(fit)$bf
    
  chains <- posterior(fit, iterations = 1000)  # get posterior probabilities
  showMerkm_givenGS <- chains[,"pi[2,1]"] / chains[,"pi[*,1]"]  # compute ratio for GS
  showMerkm_givenGY <- chains[,"pi[2,2]"] / chains[,"pi[*,2]"]  # compute ratio for GY
  cor_results[i,"prob_GSminusGY"] <- mean(mcmc(showMerkm_givenGS - showMerkm_givenGY)) # Markov Chain Monte Carlo of differences
  
  rm(imp_m, fit, chains)
}

summary(cor_results[,"lh_erl-Schulart"])

ggplot(cor_results, aes(x = `lh_erl-Schulart`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_erl-Schulart`, y=""), height = 1, width = 0, alpha = .3, size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))

# plot difference of 
summary(cor_results[,"prob_GSminusGY"])
```

### Prädiktor Klassenstufe

```{r erl Klassenstufe}
# Compute density of BFs
kl_results <- data.frame()

for (i in 1:m) {
  fit <- correlationBF(y = mice::complete(imp, i)$lh_erl,    # correlation
                       x = mice::complete(imp, i)$Klassenstufe)
  kl_results[i,"lh_erl-Klassenstufe"] <- extractBF(fit)$bf    # save BF in data frame
  
  rm(fit)
}

# show summary of BFs
summary(kl_results[,"lh_erl-Klassenstufe"])  

# plot BFs distribution
ggplot(kl_results, aes(x = `lh_erl-Klassenstufe`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_erl-Klassenstufe`, y=""), 
                            height = 1, width = 0, alpha = .3, 
                            size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))
```

### Plot der deskriptiven Daten

```{r erl plot}

###### DESCRIPTIVE PLOT ############################################### #

lh_erl_p <- p_data %>%
  dplyr::filter(!is.na(lh_erl) & !is.na(Klassenstufe)) %>%
  group_by(Klassenstufe) %>%
  mutate(length = length(lh_erl)) %>%
  summarize(lh_erl = mean(lh_erl, na.rm=T),
            length_n = mean(length)) %>%
  ungroup() %>%
  mutate(Klassenstufe = factor(Klassenstufe, levels = c("1", "1_2", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")),
         Schulart = as.factor(case_when(
                      Klassenstufe == "1" ~ "Grundschule",
                      Klassenstufe == "1_2" ~ "Grundschule",
                      Klassenstufe == "2" ~ "Grundschule",
                      Klassenstufe == "3" ~ "Grundschule",
                      Klassenstufe == "4" ~ "Grundschule",
                      TRUE ~ "Gymnasium"
         )))

ggplot(lh_erl_p, aes(x = Klassenstufe, y = lh_erl, color = Schulart)) + 
  geom_line(aes(group = NA), color = "grey", size = 1) +
  geom_point(aes(size = length_n)) +
  geom_text(aes(label = paste(round(lh_erl*100,0), "%"), vjust = 3)) +
  scale_y_continuous(limits = c(0,1), expand = c(0,0)) +
  geom_rect(aes(xmin = 0, xmax = 4.5, ymin = -Inf, ymax = Inf), fill = "pink", alpha = .01, color = NA) +
  geom_rect(aes(xmin = 4.5, xmax = 14, ymin = -Inf, ymax = Inf), fill = "#BFEFFF", alpha = .01, color = NA) +
  xlab("Klassenstufe") +
  ylab("% Häufigkeit") +
  labs(size = "Anzahl\neingegangener\nStunden") +
  theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7")) 
```


## L will Fragen

### Prädiktor Schulart

```{r haeufigkeiten wfr}
# Compute density of BFs
for (i in 1:m) {
  imp_m <- matrix(table(mice::complete(imp, i)$lh_wfr, mice::complete(imp, i)$Schulart), 2, 2)
  fit <- contingencyTableBF(imp_m, sampleType="indepMulti",fixedMargin = "cols")
  cor_results[i,"lh_wfr-Schulart"] <- extractBF(fit)$bf
    
  chains <- posterior(fit, iterations = 1000)  # get posterior probabilities
  showMerkm_givenGS <- chains[,"pi[2,1]"] / chains[,"pi[*,1]"]  # compute ratio for GS
  showMerkm_givenGY <- chains[,"pi[2,2]"] / chains[,"pi[*,2]"]  # compute ratio for GY
  cor_results[i,"prob_GSminusGY"] <- mean(mcmc(showMerkm_givenGS - showMerkm_givenGY)) # Markov Chain Monte Carlo of differences
  
  rm(imp_m, fit, chains)
}

summary(cor_results[,"lh_wfr-Schulart"])

ggplot(cor_results, aes(x = `lh_wfr-Schulart`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_wfr-Schulart`, y=""), height = 1, width = 0, alpha = .3, size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))


# plot difference of 
summary(cor_results[,"prob_GSminusGY"])
```

### Prädiktor Klassenstufe

```{r wfr Klassenstufe}
# Compute density of BFs
kl_results <- data.frame()

for (i in 1:m) {
  fit <- correlationBF(y = mice::complete(imp, i)$lh_wfr,    # correlation
                       x = mice::complete(imp, i)$Klassenstufe)
  kl_results[i,"lh_wfr-Klassenstufe"] <- extractBF(fit)$bf    # save BF in data frame
  
  rm(fit)
}

# show summary of BFs
summary(kl_results[,"lh_wfr-Klassenstufe"])  

# plot BFs distribution
ggplot(kl_results, aes(x = `lh_wfr-Klassenstufe`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_wfr-Klassenstufe`, y=""), 
                            height = 1, width = 0, alpha = .3, 
                            size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))
```

### Plot der deskriptiven Daten

```{r wfr plot}

###### DESCRIPTIVE PLOT ############################################### #

lh_wfr_p <- p_data %>%
  dplyr::filter(!is.na(lh_wfr) & !is.na(Klassenstufe)) %>%
  group_by(Klassenstufe) %>%
  mutate(length = length(lh_wfr)) %>%
  summarize(lh_wfr = mean(lh_wfr, na.rm=T),
            length_n = mean(length)) %>%
  ungroup() %>%
  mutate(Klassenstufe = factor(Klassenstufe, levels = c("1", "1_2", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")),
         Schulart = as.factor(case_when(
                      Klassenstufe == "1" ~ "Grundschule",
                      Klassenstufe == "1_2" ~ "Grundschule",
                      Klassenstufe == "2" ~ "Grundschule",
                      Klassenstufe == "3" ~ "Grundschule",
                      Klassenstufe == "4" ~ "Grundschule",
                      TRUE ~ "Gymnasium"
         )))

ggplot(lh_wfr_p, aes(x = Klassenstufe, y = lh_wfr, color = Schulart)) + 
  geom_line(aes(group = NA), color = "grey", size = 1) +
  geom_point(aes(size = length_n)) +
  geom_text(aes(label = paste(round(lh_wfr*100,0), "%"), vjust = 3)) +
  scale_y_continuous(limits = c(0,1), expand = c(0,0)) +
  geom_rect(aes(xmin = 0, xmax = 4.5, ymin = -Inf, ymax = Inf), fill = "pink", alpha = .01, color = NA) +
  geom_rect(aes(xmin = 4.5, xmax = 14, ymin = -Inf, ymax = Inf), fill = "#BFEFFF", alpha = .01, color = NA) +
  xlab("Klassenstufe") +
  ylab("% Häufigkeit") +
  labs(size = "Anzahl\neingegangener\nStunden") +
  theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7")) 
```


## L will Notation

### Prädiktor Schulart

```{r haeufigkeiten wno}
# Compute density of BFs
for (i in 1:m) {
  imp_m <- matrix(table(mice::complete(imp, i)$lh_wno, mice::complete(imp, i)$Schulart), 2, 2)
  fit <- contingencyTableBF(imp_m, sampleType="indepMulti",fixedMargin = "cols")
  cor_results[i,"lh_wno-Schulart"] <- extractBF(fit)$bf
    
  chains <- posterior(fit, iterations = 1000)  # get posterior probabilities
  showMerkm_givenGS <- chains[,"pi[2,1]"] / chains[,"pi[*,1]"]  # compute ratio for GS
  showMerkm_givenGY <- chains[,"pi[2,2]"] / chains[,"pi[*,2]"]  # compute ratio for GY
  cor_results[i,"prob_GSminusGY"] <- mean(mcmc(showMerkm_givenGS - showMerkm_givenGY)) # Markov Chain Monte Carlo of differences
  
  rm(imp_m, fit, chains)
}

summary(cor_results[,"lh_wno-Schulart"])

ggplot(cor_results, aes(x = `lh_wno-Schulart`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_wno-Schulart`, y=""), height = 1, width = 0, alpha = .3, size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))

# plot difference of 
summary(cor_results[,"prob_GSminusGY"])
```

### Prädiktor Klassenstufe

```{r wno Klassenstufe}
# Compute density of BFs
kl_results <- data.frame()

for (i in 1:m) {
  fit <- correlationBF(y = mice::complete(imp, i)$lh_wno,    # correlation
                       x = mice::complete(imp, i)$Klassenstufe)
  kl_results[i,"lh_wno-Klassenstufe"] <- extractBF(fit)$bf    # save BF in data frame
  
  rm(fit)
}

# show summary of BFs
summary(kl_results[,"lh_wno-Klassenstufe"])  

# plot BFs distribution
ggplot(kl_results, aes(x = `lh_wno-Klassenstufe`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_wno-Klassenstufe`, y=""), 
                            height = 1, width = 0, alpha = .3, 
                            size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))
```

### Plot der deskriptiven Daten

```{r wno plot}

###### DESCRIPTIVE PLOT ############################################### #

lh_wno_p <- p_data %>%
  dplyr::filter(!is.na(lh_wno) & !is.na(Klassenstufe)) %>%
  group_by(Klassenstufe) %>%
  mutate(length = length(lh_wno)) %>%
  summarize(lh_wno = mean(lh_wno, na.rm=T),
            length_n = mean(length)) %>%
  ungroup() %>%
  mutate(Klassenstufe = factor(Klassenstufe, levels = c("1", "1_2", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")),
         Schulart = as.factor(case_when(
                      Klassenstufe == "1" ~ "Grundschule",
                      Klassenstufe == "1_2" ~ "Grundschule",
                      Klassenstufe == "2" ~ "Grundschule",
                      Klassenstufe == "3" ~ "Grundschule",
                      Klassenstufe == "4" ~ "Grundschule",
                      TRUE ~ "Gymnasium"
         )))

ggplot(lh_wno_p, aes(x = Klassenstufe, y = lh_wno, color = Schulart)) + 
  geom_line(aes(group = NA), color = "grey", size = 1) +
  geom_point(aes(size = length_n)) +
  geom_text(aes(label = paste(round(lh_wno*100,0), "%"), vjust = 3)) +
  scale_y_continuous(limits = c(0,1), expand = c(0,0)) +
  geom_rect(aes(xmin = 0, xmax = 4.5, ymin = -Inf, ymax = Inf), fill = "pink", alpha = .01, color = NA) +
  geom_rect(aes(xmin = 4.5, xmax = 14, ymin = -Inf, ymax = Inf), fill = "#BFEFFF", alpha = .01, color = NA) +
  xlab("Klassenstufe") +
  ylab("% Häufigkeit") +
  labs(size = "Anzahl\neingegangener\nStunden") +
  theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7")) 
```


## L achtet auf Notation

### Prädiktor Schulart

```{r haeufigkeiten ano}
# Compute density of BFs
for (i in 1:m) {
  imp_m <- matrix(table(mice::complete(imp, i)$lh_ano, mice::complete(imp, i)$Schulart), 2, 2)
  fit <- contingencyTableBF(imp_m, sampleType="indepMulti",fixedMargin = "cols")
  cor_results[i,"lh_ano-Schulart"] <- extractBF(fit)$bf
    
  chains <- posterior(fit, iterations = 1000)  # get posterior probabilities
  showMerkm_givenGS <- chains[,"pi[2,1]"] / chains[,"pi[*,1]"]  # compute ratio for GS
  showMerkm_givenGY <- chains[,"pi[2,2]"] / chains[,"pi[*,2]"]  # compute ratio for GY
  cor_results[i,"prob_GSminusGY"] <- mean(mcmc(showMerkm_givenGS - showMerkm_givenGY)) # Markov Chain Monte Carlo of differences
  
  rm(imp_m, fit, chains)
}

summary(cor_results[,"lh_ano-Schulart"])

ggplot(cor_results, aes(x = `lh_ano-Schulart`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_ano-Schulart`, y=""), height = 1, width = 0, alpha = .3, size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))

# plot difference of 
summary(cor_results[,"prob_GSminusGY"])
```

### Prädiktor Klassenstufe

```{r ano Klassenstufe}
# Compute density of BFs
kl_results <- data.frame()

for (i in 1:m) {
  fit <- correlationBF(y = mice::complete(imp, i)$lh_ano,    # correlation
                       x = mice::complete(imp, i)$Klassenstufe)
  kl_results[i,"lh_ano-Klassenstufe"] <- extractBF(fit)$bf    # save BF in data frame
  
  rm(fit)
}

# show summary of BFs
summary(kl_results[,"lh_ano-Klassenstufe"])  

# plot BFs distribution
ggplot(kl_results, aes(x = `lh_ano-Klassenstufe`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_ano-Klassenstufe`, y=""), 
                            height = 1, width = 0, alpha = .3, 
                            size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))
```

### Plot der deskriptiven Daten

```{r ano plot}

###### DESCRIPTIVE PLOT ############################################### #

lh_ano_p <- p_data %>%
  dplyr::filter(!is.na(lh_ano) & !is.na(Klassenstufe)) %>%
  group_by(Klassenstufe) %>%
  mutate(length = length(lh_ano)) %>%
  summarize(lh_ano = mean(lh_ano, na.rm=T),
            length_n = mean(length)) %>%
  ungroup() %>%
  mutate(Klassenstufe = factor(Klassenstufe, levels = c("1", "1_2", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")),
         Schulart = as.factor(case_when(
                      Klassenstufe == "1" ~ "Grundschule",
                      Klassenstufe == "1_2" ~ "Grundschule",
                      Klassenstufe == "2" ~ "Grundschule",
                      Klassenstufe == "3" ~ "Grundschule",
                      Klassenstufe == "4" ~ "Grundschule",
                      TRUE ~ "Gymnasium"
         )))

ggplot(lh_ano_p, aes(x = Klassenstufe, y = lh_ano, color = Schulart)) + 
  geom_line(aes(group = NA), color = "grey", size = 1) +
  geom_point(aes(size = length_n)) +
  geom_text(aes(label = paste(round(lh_ano*100,0), "%"), vjust = 3)) +
  scale_y_continuous(limits = c(0,1), expand = c(0,0)) +
  geom_rect(aes(xmin = 0, xmax = 4.5, ymin = -Inf, ymax = Inf), fill = "pink", alpha = .01, color = NA) +
  geom_rect(aes(xmin = 4.5, xmax = 14, ymin = -Inf, ymax = Inf), fill = "#BFEFFF", alpha = .01, color = NA) +
  xlab("Klassenstufe") +
  ylab("% Häufigkeit") +
  labs(size = "Anzahl\neingegangener\nStunden") +
  theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7")) 

```




## L beantwortet Fragen

### Prädiktor Schulart

```{r bfr}
#### Compute BFs within informed hypotheses framework (bain) ##################################### #

### for bain: compute vcov by hand ###
# create data frame to collect var and cov for each imputation
vcov_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

mean_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

# sample size per group
samp_gr <- table(mice::complete(imp)$Schulart)


## loop over all m imputations
for(i in 1:m) {
  fit_lm <- lm(lh_bfr ~ Schulart-1, data = mice::complete(imp, i))
  
  var_lm <- summary(fit_lm)$sigma**2 # get variance of the means (VOM)
  vcov_df[i, "Grundschule"] <- var_lm/samp_gr["Grundschule"] # compute VOM per group
  vcov_df[i, "Gymnasium"] <- var_lm/samp_gr["Gymnasium"] # compute VOM per group
  
  # collect estimates of the means
  mean_df[i, "Grundschule"] <- coef(fit_lm)["SchulartGrundschule"]
  mean_df[i, "Gymnasium"] <- coef(fit_lm)["SchulartGymnasium"]
  
  rm(fit_lm, var_lm) # clean up, because we like it tidy in here
}

## make var matrices 
# compute the mean over var
vcov_df <- vcov_df %>%
        summarize_all(mean)

# create matrices
mat1 <- matrix(vcov_df$Grundschule, 1, 1)
mat2 <- matrix(vcov_df$Gymnasium, 1, 1)

variances <- list(mat1, mat2)

## compute mean of estimates
bf_data <- mean_df %>%
        summarize_all(mean)
bf_data <- as.numeric(bf_data)
names(bf_data) <- c("Grund", "Gym")

## BAIN ##### #
# generating hypotheses
hypotheses <- "Gym = Grund; Gym < Grund; Gym > Grund"

bf_hyp <- bain(bf_data, 
              hypothesis = hypotheses,
              n = samp_gr,           # size of the groups
              Sigma = variances,     # matrices of residual variances of groups
              group_parameters = 1,  # there is 1 group specific parameter (the mean in each group)
              joint_parameters = 0   # there are no parameters that apply to each of the groups (e.g. the regression coefficient of a covariate)
              )

print(bf_hyp)
print(bf_hyp$BFmatrix)

```

### Prädiktor Klassenstufe

```{r bfr Klassenstufe}
# Compute density of BFs
kl_results <- data.frame()

for (i in 1:m) {
  fit <- correlationBF(y = mice::complete(imp, i)$lh_bfr,    # correlation
                       x = mice::complete(imp, i)$Klassenstufe)
  kl_results[i,"lh_bfr-Klassenstufe"] <- extractBF(fit)$bf    # save BF in data frame
  
  rm(fit)
}

# show summary of BFs
summary(kl_results[,"lh_bfr-Klassenstufe"])  

# plot BFs distribution
ggplot(kl_results, aes(x = `lh_bfr-Klassenstufe`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `lh_bfr-Klassenstufe`, y=""), 
                            height = 1, width = 0, alpha = .3, 
                            size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))
```

### Plot der deskriptiven Daten

```{r bfr plot}
###### DESCRIPTIVE PLOT ############################################### #

lh_bfr_p <- p_data %>%
  dplyr::filter(!is.na(lh_bfr) & !is.na(Klassenstufe)) %>%
  group_by(Klassenstufe) %>%
  mutate(length = length(lh_bfr)) %>%
  summarize(lh_bfr = mean(lh_bfr, na.rm=T),
            length_n = mean(length)) %>%
  ungroup() %>%
  mutate(Klassenstufe = factor(Klassenstufe, levels = c("1", "1_2", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")),
         Schulart = as.factor(case_when(
                      Klassenstufe == "1" ~ "Grundschule",
                      Klassenstufe == "1_2" ~ "Grundschule",
                      Klassenstufe == "2" ~ "Grundschule",
                      Klassenstufe == "3" ~ "Grundschule",
                      Klassenstufe == "4" ~ "Grundschule",
                      TRUE ~ "Gymnasium"
         )))

ggplot(lh_bfr_p, aes(x = Klassenstufe, y = lh_bfr, color = Schulart)) + 
  geom_line(aes(group = NA), color = "grey", size = 1) +
  geom_point(aes(size = length_n)) +
  geom_text(aes(label = round(lh_bfr, 2), vjust = 3)) +
  scale_y_continuous(limits = c(0,(max(lh_bfr_p$lh_bfr)*1.1)), expand = c(0,0)) +
  geom_rect(aes(xmin = 0, xmax = 4.5, ymin = -Inf, ymax = Inf), fill = "pink", alpha = .01, color = NA) +
  geom_rect(aes(xmin = 4.5, xmax = 14, ymin = -Inf, ymax = Inf), fill = "#BFEFFF", alpha = .01, color = NA) +
  xlab("Klassenstufe") +
  ylab("∅ absolute Häufigkeit") +
  labs(size = "Anzahl\neingegangener\nStunden") +
  theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7")) 
```


## SuS sind aufmerksam

### Prädiktor Schulart

```{r auf}
#### Compute BFs within informed hypotheses framework (bain) ##################################### #

### for bain: compute vcov by hand ###
# create data frame to collect var and cov for each imputation
vcov_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

mean_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

# sample size per group
samp_gr <- table(mice::complete(imp)$Schulart)


## loop over all m imputations
for(i in 1:m) {
  fit_lm <- lm(sh_auf ~ Schulart-1, data = mice::complete(imp, i))
  
  var_lm <- summary(fit_lm)$sigma**2 # get variance of the means (VOM)
  vcov_df[i, "Grundschule"] <- var_lm/samp_gr["Grundschule"] # compute VOM per group
  vcov_df[i, "Gymnasium"] <- var_lm/samp_gr["Gymnasium"] # compute VOM per group
  
  # collect estimates of the means
  mean_df[i, "Grundschule"] <- coef(fit_lm)["SchulartGrundschule"]
  mean_df[i, "Gymnasium"] <- coef(fit_lm)["SchulartGymnasium"]
  
  rm(fit_lm, var_lm) # clean up, because we like it tidy in here
}

## make var matrices 
# compute the mean over var
vcov_df <- vcov_df %>%
        summarize_all(mean)

# create matrices
mat1 <- matrix(vcov_df$Grundschule, 1, 1)
mat2 <- matrix(vcov_df$Gymnasium, 1, 1)

variances <- list(mat1, mat2)

## compute mean of estimates
bf_data <- mean_df %>%
        summarize_all(mean)
bf_data <- as.numeric(bf_data)
names(bf_data) <- c("Grund", "Gym")

## BAIN ##### #
# generating hypotheses
hypotheses <- "Gym = Grund; Gym < Grund; Gym > Grund"

bf_hyp <- bain(bf_data, 
              hypothesis = hypotheses,
              n = samp_gr,           # size of the groups
              Sigma = variances,     # matrices of residual variances of groups
              group_parameters = 1,  # there is 1 group specific parameter (the mean in each group)
              joint_parameters = 0   # there are no parameters that apply to each of the groups (e.g. the regression coefficient of a covariate)
              )

print(bf_hyp)
print(bf_hyp$BFmatrix)


```

### Prädiktor Klassenstufe

```{r sh_auf Klassenstufe}
# Compute density of BFs
kl_results <- data.frame()

for (i in 1:m) {
  fit <- correlationBF(y = mice::complete(imp, i)$sh_auf,    # correlation
                       x = mice::complete(imp, i)$Klassenstufe)
  kl_results[i,"sh_auf-Klassenstufe"] <- extractBF(fit)$bf    # save BF in data frame
  
  rm(fit)
}

# show summary of BFs
summary(kl_results[,"sh_auf-Klassenstufe"])  

# plot BFs distribution
ggplot(kl_results, aes(x = `sh_auf-Klassenstufe`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `sh_auf-Klassenstufe`, y=""), 
                            height = 1, width = 0, alpha = .3, 
                            size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))
```

### Plot der deskriptiven Daten

```{r sh_auf plot}

###### DESCRIPTIVE PLOT ############################################### #

sh_auf_p <- p_data %>%
  dplyr::filter(!is.na(sh_auf) & !is.na(Klassenstufe)) %>%
  group_by(Klassenstufe) %>%
  mutate(length = length(sh_auf)) %>%
  summarize(sh_auf = mean(sh_auf, na.rm=T),
            length_n = mean(length)) %>%
  ungroup() %>%
  mutate(Klassenstufe = factor(Klassenstufe, levels = c("1", "1_2", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")),
         Schulart = as.factor(case_when(
                      Klassenstufe == "1" ~ "Grundschule",
                      Klassenstufe == "1_2" ~ "Grundschule",
                      Klassenstufe == "2" ~ "Grundschule",
                      Klassenstufe == "3" ~ "Grundschule",
                      Klassenstufe == "4" ~ "Grundschule",
                      TRUE ~ "Gymnasium"
         )))

ggplot(sh_auf_p, aes(x = Klassenstufe, y = sh_auf, color = Schulart)) + 
  geom_line(aes(group = NA), color = "grey", size = 1) +
  geom_point(aes(size = length_n)) +
  geom_text(aes(label = round(sh_auf,1), vjust = -3)) +
  scale_y_continuous(limits = c(1,5), expand = c(0,0)) +
  geom_rect(aes(xmin = 0, xmax = 4.5, ymin = -Inf, ymax = Inf), fill = "pink", alpha = .01, color = NA) +
  geom_rect(aes(xmin = 4.5, xmax = 14, ymin = -Inf, ymax = Inf), fill = "#BFEFFF", alpha = .01, color = NA) +
  xlab("Klassenstufe") +
  ylab("Zustimmung (Likert Item)") +
  labs(size = "Anzahl\neingegangener\nStunden") +
  theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7")) 
```

## SuS melden sich

### Prädiktor Schulart

```{r mel}
#### Compute BFs within informed hypotheses framework (bain) ##################################### #

### for bain: compute vcov by hand ###
# create data frame to collect var and cov for each imputation
vcov_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

mean_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

# sample size per group
samp_gr <- table(mice::complete(imp)$Schulart)


## loop over all m imputations
for(i in 1:m) {
  fit_lm <- lm(sh_mel ~ Schulart-1, data = mice::complete(imp, i))
  
  var_lm <- summary(fit_lm)$sigma**2 # get variance of the means (VOM)
  vcov_df[i, "Grundschule"] <- var_lm/samp_gr["Grundschule"] # compute VOM per group
  vcov_df[i, "Gymnasium"] <- var_lm/samp_gr["Gymnasium"] # compute VOM per group
  
  # collect estimates of the means
  mean_df[i, "Grundschule"] <- coef(fit_lm)["SchulartGrundschule"]
  mean_df[i, "Gymnasium"] <- coef(fit_lm)["SchulartGymnasium"]
  
  rm(fit_lm, var_lm) # clean up, because we like it tidy in here
}

## make var matrices 
# compute the mean over var
vcov_df <- vcov_df %>%
        summarize_all(mean)

# create matrices
mat1 <- matrix(vcov_df$Grundschule, 1, 1)
mat2 <- matrix(vcov_df$Gymnasium, 1, 1)

variances <- list(mat1, mat2)

## compute mean of estimates
bf_data <- mean_df %>%
        summarize_all(mean)
bf_data <- as.numeric(bf_data)
names(bf_data) <- c("Grund", "Gym")

## BAIN ##### #
# generating hypotheses
hypotheses <- "Gym = Grund; Gym < Grund; Gym > Grund"

bf_hyp <- bain(bf_data, 
              hypothesis = hypotheses,
              n = samp_gr,           # size of the groups
              Sigma = variances,     # matrices of residual variances of groups
              group_parameters = 1,  # there is 1 group specific parameter (the mean in each group)
              joint_parameters = 0   # there are no parameters that apply to each of the groups (e.g. the regression coefficient of a covariate)
              )

print(bf_hyp)
print(bf_hyp$BFmatrix)
```

### Prädiktor Klassenstufe

```{r sh_mel Klassenstufe}
# Compute density of BFs
kl_results <- data.frame()

for (i in 1:m) {
  fit <- correlationBF(y = mice::complete(imp, i)$sh_mel,    # correlation
                       x = mice::complete(imp, i)$Klassenstufe)
  kl_results[i,"sh_mel-Klassenstufe"] <- extractBF(fit)$bf    # save BF in data frame
  
  rm(fit)
}

# show summary of BFs
summary(kl_results[,"sh_mel-Klassenstufe"])  

# plot BFs distribution
ggplot(kl_results, aes(x = `sh_mel-Klassenstufe`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `sh_mel-Klassenstufe`, y=""), 
                            height = 1, width = 0, alpha = .3, 
                            size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))
```

### Plot der deskriptiven Daten

```{r sh_mel plot}
###### DESCRIPTIVE PLOT ############################################### #

sh_mel_p <- p_data %>%
  dplyr::filter(!is.na(sh_mel) & !is.na(Klassenstufe)) %>%
  group_by(Klassenstufe) %>%
  mutate(length = length(sh_mel)) %>%
  summarize(sh_mel = mean(sh_mel, na.rm=T),
            length_n = mean(length)) %>%
  ungroup() %>%
  mutate(Klassenstufe = factor(Klassenstufe, levels = c("1", "1_2", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")),
         Schulart = as.factor(case_when(
                      Klassenstufe == "1" ~ "Grundschule",
                      Klassenstufe == "1_2" ~ "Grundschule",
                      Klassenstufe == "2" ~ "Grundschule",
                      Klassenstufe == "3" ~ "Grundschule",
                      Klassenstufe == "4" ~ "Grundschule",
                      TRUE ~ "Gymnasium"
         )))

ggplot(sh_mel_p, aes(x = Klassenstufe, y = sh_mel, color = Schulart)) + 
  geom_line(aes(group = NA), color = "grey", size = 1) +
  geom_point(aes(size = length_n)) +
  geom_text(aes(label = round(sh_mel, 2), vjust = 3)) +
  scale_y_continuous(limits = c(0,(max(sh_mel_p$sh_mel)*1.1)), expand = c(0,0)) +
  geom_rect(aes(xmin = 0, xmax = 4.5, ymin = -Inf, ymax = Inf), fill = "pink", alpha = .01, color = NA) +
  geom_rect(aes(xmin = 4.5, xmax = 14, ymin = -Inf, ymax = Inf), fill = "#BFEFFF", alpha = .01, color = NA) +
  xlab("Klassenstufe") +
  ylab("∅ absolute Häufigkeit") +
  labs(size = "Anzahl\neingegangener\nStunden") +
  theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7")) 
```


## SuS fragen

### Prädiktor Schulart

```{r fra}
#### Compute BFs within informed hypotheses framework (bain) ##################################### #

### for bain: compute vcov by hand ###
# create data frame to collect var and cov for each imputation
vcov_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

mean_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

# sample size per group
samp_gr <- table(mice::complete(imp)$Schulart)


## loop over all m imputations
for(i in 1:m) {
  fit_lm <- lm(sh_fra ~ Schulart-1, data = mice::complete(imp, i))
  
  var_lm <- summary(fit_lm)$sigma**2 # get variance of the means (VOM)
  vcov_df[i, "Grundschule"] <- var_lm/samp_gr["Grundschule"] # compute VOM per group
  vcov_df[i, "Gymnasium"] <- var_lm/samp_gr["Gymnasium"] # compute VOM per group
  
  # collect estimates of the means
  mean_df[i, "Grundschule"] <- coef(fit_lm)["SchulartGrundschule"]
  mean_df[i, "Gymnasium"] <- coef(fit_lm)["SchulartGymnasium"]
  
  rm(fit_lm, var_lm) # clean up, because we like it tidy in here
}

## make var matrices 
# compute the mean over var
vcov_df <- vcov_df %>%
        summarize_all(mean)

# create matrices
mat1 <- matrix(vcov_df$Grundschule, 1, 1)
mat2 <- matrix(vcov_df$Gymnasium, 1, 1)

variances <- list(mat1, mat2)

## compute mean of estimates
bf_data <- mean_df %>%
        summarize_all(mean)
bf_data <- as.numeric(bf_data)
names(bf_data) <- c("Grund", "Gym")

## BAIN ##### #
# generating hypotheses
hypotheses <- "Gym = Grund; Gym < Grund; Gym > Grund"

bf_hyp <- bain(bf_data, 
              hypothesis = hypotheses,
              n = samp_gr,           # size of the groups
              Sigma = variances,     # matrices of residual variances of groups
              group_parameters = 1,  # there is 1 group specific parameter (the mean in each group)
              joint_parameters = 0   # there are no parameters that apply to each of the groups (e.g. the regression coefficient of a covariate)
              )

print(bf_hyp)
print(bf_hyp$BFmatrix)

```

### Prädiktor Klassenstufe

```{r sh_fra Klassenstufe}
# Compute density of BFs
kl_results <- data.frame()

for (i in 1:m) {
  fit <- correlationBF(y = mice::complete(imp, i)$sh_fra,    # correlation
                       x = mice::complete(imp, i)$Klassenstufe)
  kl_results[i,"sh_fra-Klassenstufe"] <- extractBF(fit)$bf    # save BF in data frame
  
  rm(fit)
}

# show summary of BFs
summary(kl_results[,"sh_fra-Klassenstufe"])  

# plot BFs distribution
ggplot(kl_results, aes(x = `sh_fra-Klassenstufe`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `sh_fra-Klassenstufe`, y=""), 
                            height = 1, width = 0, alpha = .3, 
                            size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))
```

### Plot der deskriptiven Daten

```{r sh_fra plot}
###### DESCRIPTIVE PLOT ############################################### #

sh_fra_p <- p_data %>%
  dplyr::filter(!is.na(sh_fra) & !is.na(Klassenstufe)) %>%
  group_by(Klassenstufe) %>%
  mutate(length = length(sh_fra)) %>%
  summarize(sh_fra = mean(sh_fra, na.rm=T),
            length_n = mean(length)) %>%
  ungroup() %>%
  mutate(Klassenstufe = factor(Klassenstufe, levels = c("1", "1_2", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")),
         Schulart = as.factor(case_when(
                      Klassenstufe == "1" ~ "Grundschule",
                      Klassenstufe == "1_2" ~ "Grundschule",
                      Klassenstufe == "2" ~ "Grundschule",
                      Klassenstufe == "3" ~ "Grundschule",
                      Klassenstufe == "4" ~ "Grundschule",
                      TRUE ~ "Gymnasium"
         )))

ggplot(sh_fra_p, aes(x = Klassenstufe, y = sh_fra, color = Schulart)) + 
  geom_line(aes(group = NA), color = "grey", size = 1) +
  geom_point(aes(size = length_n)) +
  geom_text(aes(label = round(sh_fra, 2), vjust = 3)) +
  scale_y_continuous(limits = c(0,(max(sh_fra_p$sh_fra)*1.1)), expand = c(0,0)) +
  geom_rect(aes(xmin = 0, xmax = 4.5, ymin = -Inf, ymax = Inf), fill = "pink", alpha = .01, color = NA) +
  geom_rect(aes(xmin = 4.5, xmax = 14, ymin = -Inf, ymax = Inf), fill = "#BFEFFF", alpha = .01, color = NA) +
  xlab("Klassenstufe") +
  ylab("∅ absolute Häufigkeit") +
  labs(size = "Anzahl\neingegangener\nStunden") +
  theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7")) 

```


## SuS notieren

### Prädiktor Schulart

```{r not}
#### Compute BFs within informed hypotheses framework (bain) ##################################### #

### for bain: compute vcov by hand ###
# create data frame to collect var and cov for each imputation
vcov_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

mean_df <- data.frame(Grundschule = as.numeric(),
                      Gymnasium = as.numeric()
                      )

# sample size per group
samp_gr <- table(mice::complete(imp)$Schulart)


## loop over all m imputations
for(i in 1:m) {
  fit_lm <- lm(sh_not ~ Schulart-1, data = mice::complete(imp, i))
  
  var_lm <- summary(fit_lm)$sigma**2 # get variance of the means (VOM)
  vcov_df[i, "Grundschule"] <- var_lm/samp_gr["Grundschule"] # compute VOM per group
  vcov_df[i, "Gymnasium"] <- var_lm/samp_gr["Gymnasium"] # compute VOM per group
  
  # collect estimates of the means
  mean_df[i, "Grundschule"] <- coef(fit_lm)["SchulartGrundschule"]
  mean_df[i, "Gymnasium"] <- coef(fit_lm)["SchulartGymnasium"]
  
  rm(fit_lm, var_lm) # clean up, because we like it tidy in here
}

## make var matrices 
# compute the mean over var
vcov_df <- vcov_df %>%
        summarize_all(mean)

# create matrices
mat1 <- matrix(vcov_df$Grundschule, 1, 1)
mat2 <- matrix(vcov_df$Gymnasium, 1, 1)

variances <- list(mat1, mat2)

## compute mean of estimates
bf_data <- mean_df %>%
        summarize_all(mean)
bf_data <- as.numeric(bf_data)
names(bf_data) <- c("Grund", "Gym")

## BAIN ##### #
# generating hypotheses
hypotheses <- "Gym = Grund; Gym < Grund; Gym > Grund"

bf_hyp <- bain(bf_data, 
              hypothesis = hypotheses,
              n = samp_gr,           # size of the groups
              Sigma = variances,     # matrices of residual variances of groups
              group_parameters = 1,  # there is 1 group specific parameter (the mean in each group)
              joint_parameters = 0   # there are no parameters that apply to each of the groups (e.g. the regression coefficient of a covariate)
              )

print(bf_hyp)
print(bf_hyp$BFmatrix)

```

### Prädiktor Klassenstufe

```{r sh_not Klassenstufe}
# Compute density of BFs
kl_results <- data.frame()

for (i in 1:m) {
  fit <- correlationBF(y = mice::complete(imp, i)$sh_not,    # correlation
                       x = mice::complete(imp, i)$Klassenstufe)
  kl_results[i,"sh_not-Klassenstufe"] <- extractBF(fit)$bf    # save BF in data frame
  
  rm(fit)
}

# show summary of BFs
summary(kl_results[,"sh_not-Klassenstufe"])  

# plot BFs distribution
ggplot(kl_results, aes(x = `sh_not-Klassenstufe`)) +
                geom_density(alpha = .3, fill = "#b4a069", color = NA) +
                geom_jitter(aes(x = `sh_not-Klassenstufe`, y=""), 
                            height = 1, width = 0, alpha = .3, 
                            size = 2.5, fill = "#b4a069", color = "#b4a069") +
                geom_vline(xintercept = (1/3), color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                geom_vline(xintercept = 3, color = "red", alpha = .4, 
                           size = 2, linetype = "dashed") +
                scale_x_continuous(expand = c(0, 0), trans = 'log10') +
                scale_y_discrete(expand = c(0, 0)) +
                ylab("% Häufigkeit") +
                xlab("BF [log10]") +
                theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7"))
```

### Plot der deskriptiven Daten

```{r sh_not plot}
###### DESCRIPTIVE PLOT ############################################### #

sh_not_p <- p_data %>%
  dplyr::filter(!is.na(sh_not) & !is.na(Klassenstufe)) %>%
  group_by(Klassenstufe) %>%
  mutate(length = length(sh_not)) %>%
  summarize(sh_not = mean(sh_not, na.rm=T),
            length_n = mean(length)) %>%
  ungroup() %>%
  mutate(Klassenstufe = factor(Klassenstufe, levels = c("1", "1_2", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")),
         Schulart = as.factor(case_when(
                      Klassenstufe == "1" ~ "Grundschule",
                      Klassenstufe == "1_2" ~ "Grundschule",
                      Klassenstufe == "2" ~ "Grundschule",
                      Klassenstufe == "3" ~ "Grundschule",
                      Klassenstufe == "4" ~ "Grundschule",
                      TRUE ~ "Gymnasium"
         )))

ggplot(sh_not_p, aes(x = Klassenstufe, y = sh_not, color = Schulart)) + 
  geom_line(aes(group = NA), color = "grey", size = 1) +
  geom_point(aes(size = length_n)) +
  geom_text(aes(label = paste(round(sh_not,0), "%"), vjust = 3)) +
  scale_y_continuous(limits = c(0,(max(sh_not_p$sh_not)*1.1)), expand = c(0,0)) +
  geom_rect(aes(xmin = 0, xmax = 4.5, ymin = -Inf, ymax = Inf), fill = "pink", alpha = .01, color = NA) +
  geom_rect(aes(xmin = 4.5, xmax = 14, ymin = -Inf, ymax = Inf), fill = "#BFEFFF", alpha = .01, color = NA) +
  xlab("Klassenstufe") +
  ylab("∅ absolute Häufigkeit") +
  labs(size = "Anzahl\neingegangener\nStunden") +
  theme_light() +
                theme(axis.line = element_line(colour = "#696f71"),
                      panel.grid.major = element_blank(),
                      panel.grid.minor = element_blank(),
                      panel.border = element_blank(),
                      panel.background = element_rect(fill = "#f6f7f7")) 
```


# Korrelationen

Bitte mit der Maus über die einzelnen Punkte fahren, um zu erfahren um welche Korrelation es sich handelt.

```{r korr1, fig.width=11, fig.height=11}
p_dataGS <- p_data %>%
  filter(Schulart == "Grundschule")

p_dataGY <- p_data %>%
  filter(Schulart == "Gymnasium")

impGS <- mice(p_dataGS, 
            maxit = maxit, 
            m = m,
            meth = meth,
            pred = pred,
            seed = 666,
            printFlag = F
            )

impGY <- mice(p_dataGY, 
            maxit = maxit, 
            m = m,
            meth = meth,
            pred = pred,
            seed = 666,
            printFlag = F
            )

corGS <- miceadds::micombine.cor(impGS, variables = c("lh_ank", "lh_auf", "lh_nen", 
                                                      "lh_sch", "lh_erl", "lh_wfr", 
                                                      "lh_wno", "lh_ano", "lh_bfr", 
                                                      "sh_auf", "sh_mel", "sh_fra", 
                                                      "sh_not"))

corGY <- miceadds::micombine.cor(impGY, variables = c("lh_ank", "lh_auf", "lh_nen", 
                                                      "lh_sch", "lh_erl", "lh_wfr", 
                                                      "lh_wno", "lh_ano", "lh_bfr", 
                                                      "sh_auf", "sh_mel", "sh_fra", 
                                                      "sh_not"))

corGS <- corGS[1:78,] %>%
    mutate(Korrelation = paste(variable1, variable2, sep="-"),
           rGS = round(r, digits = 3)) %>%
    dplyr::select(Korrelation, rGS)

corGY <- corGY[1:78,] %>%
    mutate(Korrelation = paste(variable1, variable2, sep="-"),
           rGY = round(r, digits = 3)) %>%
    dplyr::select(Korrelation, rGY)

corGSGY <- full_join(corGS, corGY, by = "Korrelation")


# library(ggrepel)
# ggplot(corGSGY, aes(x=rGS, y=rGY, color = Korrelation, label = Korrelation)) +
#   geom_point() +
#   scale_x_continuous(limits = c(0,1)) +
#   scale_y_continuous(limits = c(0,1)) +
#   geom_abline(intercept = 0, slope = 1) +
#   geom_label_repel() +
#   theme(legend.position = "none")


library(plotly)
axis_def <- list(range = c(-.4, 1),
                 dtick = 0.25,
                 automargin = TRUE)

plot_ly() %>%
  add_trace(
    x = c(-.4,-.4,1),
    y = c(-.4,  1, 1),
    name = "Korrelation in GY größer",
    type = 'scatter',
    fill = 'toself',
    fillcolor = '#BFEFFF',
    opacity = .4,
    hoveron = 'points',
    marker = list(
      color = '#BFEFFF',
      opacity = 0),
    line = list(
      color = '#BFEFFF'),
    text = "",
    hoverinfo = ''
    ) %>%
  add_trace(
    x = c(-.4, 1,1),
    y = c(-.4,-.4, 1),
    name = "Korrelation in GS größer",
    type = 'scatter',
    fill = 'toself',
    fillcolor = 'pink',
    opacity = .4,
    hoveron = 'points',
    marker = list(
      color = 'pink',
      opacity = 0),
    line = list(
      color = 'pink'),
    text = "",
    hoverinfo = ''
    ) %>%
  add_trace(
    data = corGSGY, 
    x = ~rGS, 
    y = ~rGY,
    type = "scatter", 
    mode = "markers",
    marker = list(
      color = "darkgrey",
      opacity = .85
    ),
    name = "Korrelationskoeffizient in GY und GS",
    text = ~paste("Korrelation: ", Korrelation, 
                  '<br>r<sub>GY</sub>= ', rGY, 
                  '<br>r<sub>GS</sub>= ', rGS)) %>%
  layout(
    xaxis = axis_def,
    yaxis = axis_def,
    autosize = F, 
    width = 800, 
    height = 800,
    legend = list(orientation = 'h',
                  x = 0,
                  y = 1))


pander(corGSGY)


miceadds::micombine.cor(imp45, variables = c("beg_hw_min", "dau_hw_min"))
miceadds::micombine.cor(imp90, variables = c("beg_hw_min", "dau_hw_min"))
```



```{r dichotome korrelationen 1, fig.width=11, fig.height=11}
library(DescTools)
cor_var <- c("lh_ank", "lh_auf", "lh_nen", "lh_sch", "lh_erl", "lh_wfr", "lh_wno", "lh_ano")
cor_datGS <- data.frame()
cor_datGY <- data.frame()

# Grundschule
for (n_i in 1:i) {                # über alle Imputationen
  for (cor_1 in 1:7) {            # Kombinationen aller dichotomen
    for (cor_2 in (cor_1+1):8) {  # Variablen erstellen
      tmp <- eval(parse(text = paste0("YuleQ(", 
                         "mice::complete(impGS, ", n_i, ")$", cor_var[cor_1],
                         ", ",
                         "mice::complete(impGS, ", n_i, ")$", cor_var[cor_2],
                         ")",
                         sep="")    # für jeden vollständigen Datensatz
                        )           # mit einer bestimmten Var-Kombination
                  )                 # YulesQ berechnen
      
      # Wert in Datensatz speichern
      cor_datGS[n_i, paste0(cor_var[cor_1], "-", cor_var[cor_2])] <- tmp
      rm(tmp)
    }
  }
}

# Gymnasium
for (n_i in 1:i) {                # über alle Imputationen
  for (cor_1 in 1:7) {            # Kombinationen aller dichotomen
    for (cor_2 in (cor_1+1):8) {  # Variablen erstellen
      tmp <- eval(parse(text = paste0("YuleQ(", 
                         "mice::complete(impGY, ", n_i, ")$", cor_var[cor_1],
                         ", ",
                         "mice::complete(impGY, ", n_i, ")$", cor_var[cor_2],
                         ")",
                         sep="")    # für jeden vollständigen Datensatz
                        )           # mit einer bestimmten Var-Kombination
                  )                 # YulesQ berechnen
      
      # Wert in Datensatz speichern
      cor_datGY[n_i, paste0(cor_var[cor_1], "-", cor_var[cor_2])] <- tmp
      rm(tmp)
    }
  }
}
```
\

In order to combine correlation estimates via Rubin's Rules we first have to apply Fisher-Transformation for Correlation to z-Score as correlations are not normally distributed and then transform the values back to correlation coefficients.

```{r dichotome korrelationen 2, fig.width=11, fig.height=11}
# apply Fisher-Transformation
cor_dat_fisherGS <- FisherZ(cor_datGS)
cor_dat_fisherGY <- FisherZ(cor_datGY)

# combine estimates 
cor_dat_fisherGS <- cor_dat_fisherGS %>%
                      summarise_all(mean)
cor_dat_fisherGY <- cor_dat_fisherGY %>%
                      summarise_all(mean)

# transform back to correlation coefficients
cor_datGS <- FisherZInv(cor_dat_fisherGS)
cor_datGY <- FisherZInv(cor_dat_fisherGY)

# pivot into long data format, for later joining
cor_datGS_l <- pivot_longer(cor_datGS, names_to = "Korrelation", values_to = "rGS", cols = 1:28) 
cor_datGY_l <- pivot_longer(cor_datGY, names_to = "Korrelation", values_to = "rGY", cols = 1:28) 



# p_data_dm <- p_data %>%
#   dplyr::select(lh_ank, lh_auf, lh_sch, lh_erl, lh_wfr, lh_wno, lh_ano)
# dicho_r_m <- data.frame()
# 
# # Correlation matrix & visualization
# for(i in 1:7) {
#   for(j in 1:7){
#     # print(c(i,j))
#     tmp <- matrix(table(p_data_dm[,i], p_data_dm[,j]), 2, 2)
#     dicho_r_m[j,i] <- Yule(tmp)                                   #Alternative phi
#     dicho_r_m[i,j] <- Yule(tmp)                                   #Alternative phi
#   }
# }
# 
# names(dicho_r_m) <- c("lh_ank", "lh_auf", "lh_sch", "lh_erl", "lh_wfr", "lh_wno", "lh_ano")
# row.names(dicho_r_m) <- c("lh_ank", "lh_auf", "lh_sch", "lh_erl", "lh_wfr", "lh_wno", "lh_ano")
# # corrgram(dicho_r_m, type = "cor", lower.panel = "panel.pie", upper.panel = "panel.cor")
# 
# # GS vs. GYM
# 
# dicho_r_gs <- data.frame(cor_gs = NA, comb = NA)
# dicho_r_gs <- dicho_r_gs[-1,]
# 
# p_data_dm_gs <- p_data %>%
#   dplyr::filter(Schulart == "Grundschule") %>%
#   dplyr::select(lh_ank, lh_auf, lh_sch, lh_erl, lh_wfr, lh_wno, lh_ano)
# 
# for(i in 1:6) {
#   for(j in (1+i):7){
#     tmp <- matrix(table(p_data_dm_gs[,i], p_data_dm_gs[,j]), 2, 2)
#     tmp1 <-  data.frame()
#     tmp1[1, "cor_gs"] <- Yule(tmp)
#     tmp1[1, "comb"] <- paste(names(p_data_dm_gs[i]), "-", names(p_data_dm_gs[j]))
#     dicho_r_gs <- rbind(dicho_r_gs, tmp1)
#   }
# }
# 
# 
# 
# 
# dicho_r_gy <- data.frame(cor_gy = NA, comb = NA)
# dicho_r_gy <- dicho_r_gy[-1,]
# 
# p_data_dm_gy <- p_data %>%
#   dplyr::filter(Schulart == "Gymnasium") %>%
#   dplyr::select(lh_ank, lh_auf, lh_sch, lh_erl, lh_wfr, lh_wno, lh_ano)
# 
# for(i in 1:6) {
#   for(j in (1+i):7){
#     tmp <- matrix(table(p_data_dm_gy[,i], p_data_dm_gy[,j]), 2, 2)
#     tmp1 <-  data.frame()
#     tmp1[1, "cor_gy"] <- Yule(tmp)
#     tmp1[1, "comb"] <- paste(names(p_data_dm_gy[i]), "-", names(p_data_dm_gy[j]))
#     dicho_r_gy <- rbind(dicho_r_gy, tmp1)
#   }
# }
# 
# dicho_r <- full_join(dicho_r_gs, dicho_r_gy, by="comb")
# 
# 
# 
# ggplot(dicho_r, aes(x=cor_gs, y=cor_gy, color = comb, label = comb)) +
#   geom_point() +
#   scale_x_continuous(limits = c(0,1)) +
#   scale_y_continuous(limits = c(0,1)) +
#   geom_abline(intercept = 0, slope = 1) +
#   geom_label_repel() +
#   theme(legend.position = "none")
```